\maintitle{SEchangelog}{\changelog}

\subtitle{0.205.2}

\begin{itemize}
\item Logotype on the titlepage changed for our new logotype.
\item Area Attack, updated with the reverted order of X and Y.
\item Bug with the spacing around headers corrected.
\item Oaken Crown, the bearer gains Swift Reform, not the unit.
\end{itemize}

\subtitle{0.205.1}

\begin{itemize}
\item Avatar of Nature, the correct price is 630 pts.
\end{itemize}

\subtitle{0.205.0}

\begin{itemize}
\item Blue and green from 0.204 removed.
\item Standardisation of the formatting of lists.
\item Confusion between hyphen (-), en-dash (--), em-dash (---) and minus symbol (−) corrected.
\item \enquote{x} replaced with \enquote{\timess{}} as the mathematical times symbol (for example in 25\timess{}50).
\item Replace Hard Target with Hard Target (1), Last one Turn with One Turn, Catapult(X) with Catapult (X\timess{}X).
\item Beta for the Quick Reference Sheet, check it and give us feedback!
\end{itemize}

Un-nesting rulebook model rules. Models given rules that used to be nested in other rules.
\begin{itemize}
\item Light Troops and Swiftstride no longer part of Fly.
\item Fearless no longer part of Frenzy.
\item Hard Target and Light Troops no longer part of Skirmisher.
\item Fear no longer part of Terror.
\item Fearless no longer part of Unbreakable, Unstable, or Supernal.
\item Move or Fire no longer part of War Machine.
\item Not a Leader no longer part of War Platforms.
\end{itemize}

%\subtitle{General}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Army Model Rules}
%
%\begin{itemize}[label={-}]
%\item The Forest Follows, missing comma.
%\item Master Archer, small rewording.
%\item Impaling Roots, no caps for shoot.
%\end{itemize}
%
\subtitle{Kindreds and Aspects}

\begin{itemize}
\item Forest Guardian, redundant text removed
\end{itemize}
%
%\subtitle{Special Equipment}
%
%\begin{itemize}[label={-}]
%\item Curse of the Black Stag, switch Def and Att.
%\item Lifeseed Feathers, typo.
%\item Glyph of Amryl, slight rewording.
%\end{itemize}
%
%\subtitle{Characters}
%
%\begin{itemize}[label={-}]
%\item typo in the name Thicket Shepherd.
%\end{itemize}
%
%%\subtitle{Core}
%%
%%\begin{itemize}[label={-}]
%%\item 
%%\end{itemize}
%
\subtitle{Special}

\begin{itemize}
\item Blade Dancers, clarification
\end{itemize}
%
%\subtitle{Unseen Arrows}
%
%\begin{itemize}[label={-}]
%\item Sylvan Sentinels, Choice replaced with Units.
%\end{itemize}

\subtitle{Points}
\begin{itemize}
\item Drums of Cenyrn 40
\item Predator Pennant 50
\item Forest Prince Dragon Mount 440
\item Druid Dragon Mount 440
\item Avatar of Nature 630
\item Forest Ranger start 210
\item Dryads Skirmish upgrade 4
\item Wild Huntsmen Sylvan Blades 1
\item Treefather 450
\item Briar maidens start 200
- additional 35
\end{itemize}
