
\newcommand{\bloodpowers}{Blood Powers}
\newcommand{\bloodpowersInitial}{BP}

\newcommand{\bloodpowersintroduction}{%
	Vampire Counts and Vampire Courtiers may purchase a unique upgrade called Blood Power. In an army without a Bloodline (called an Independent Army), all Blood Powers are 0--1 per Army. However, in an army with a Bloodline (called Bloodline Army), only that Bloodline's powers can be taken, though these powers can be duplicated
within the army unless noted otherwise.%
}

\newcommand{\independentorbrotherhoodofthedragon}{Independent or\\ Brotherhood of the Dragon}

\newcommand{\eternalduellist}{Eternal Duellist}
\newcommand{\eternalduellistdef}{%
	The Vampire must reroll natural to-hit and to-wound rolls of \result{1} with its Close Combat Attacks.%
}
\newcommand{\monsterhunter}{Monster Hunter}
\newcommand{\monsterhunterdef}{%
	The Vampire gains \textbf{Multiple Wounds (2, against Towering Presence)}.%
}

\newcommand{\independentorvonkarnstein}{Independent or Von Karnstein}

\newcommand{\hourofthewolf}{Hour of the Wolf}
\newcommand{\hourofthewolfdef}{%
	The Vampire's unit gains \textbf{\swiftstride}. The Vampire gains \textbf{\awaken{} (\batswarms{}, \direwolves{}, \greatbats{}, \zombies{})}.%
}
\newcommand{\unbreakablewill}{Unbreakable Will}
\newcommand{\unbreakablewilldef}{%
	At the beginning of each Round of Combat, select a single friendly unit Engaged in the same Combat as the Vampire (this can be the Vampire's own unit). This unit gains \textbf{\stubborn} until the end of the Melee Phase.%
}

\newcommand{\independentorlamia}{Independent or Lamia}

\newcommand{\maskofinnocence}{Mask of Innocence}
\newcommand{\maskofinnocencedef}{%
	Enemy units in base contact with one or more Vampires with the Mask of Innocence suffer \minuss{}1 Discipline.%
}
\newcommand{\mesmerisinggaze}{Mesmerising Gaze}
\newcommand{\mesmerisinggazedef}{%
	The Vampire can cast \spellformat{\evocationspelltwo}{\evocation} as a Bound Spell with Power Level (4/8).%
}

\newcommand{\independentorstrigoi}{Independent or Strigoi}

\newcommand{\flyinghorror}{Flying Horror}
\newcommand{\flyinghorrordef}{%
	The Vampire gains \textbf{\fly{7}{14}}, \textbf{\lighttroops}, \textbf{\stormofwings} (see \hyperlink{VC3batswarms}{Bat Swarms}), and \textbf{\swiftstride}.%
}
\newcommand{\bestialbulk}{Bestial Bulk}
\newcommand{\bestialbulkdef}{%
	The Vampire gains +1 Resilience and cannot use any Weapon Enchantments or Armour Equipment. The Vampire changes its Height to Large and its base size to 40\timess{}\SI{40}{\milli\meter}. As long as the Vampire is joined to a unit of Ghasts, the Vampire gains \textbf{\scoring}. If playing Capture the Flags, the Vampire gains Scoring (no matter if joined to a unit of Ghasts or not).%
}

\newcommand{\independentornosferatu}{Independent or Nosferatu}
\newcommand{\arcaneknowledge}{Arcane Knowledge}
\newcommand{\arcaneknowledgedef}{%
	The Vampire knows the Hereditary Spell in addition to its other spells. Spells cast by the Vampire gain +\distance{6} range. This effect is decreased to +\distance{3} range for Aura spells. Bound Spells and spells without range are not affected.%
}
\newcommand{\forbiddenpath}{Forbidden Path}
\newcommand{\forbiddenpathrestriction}{Wizard Adepts and Masters only}
\newcommand{\forbiddenpathdef}{%
	A Wizard Master with this Blood Power becomes a Wizard Adept using two different Paths it has access to (it knows 2 spells from each Path). A Wizard Adept becomes a Wizard Apprentice using two different Paths it has access to (it knows 1 spell from each Path).\newline%
This Blood Power cannot be combined with Essence of a Free Mind.%
}
