
\newcommand{\vampiricbloodlines}{Vampiric Bloodlines}
\newcommand{\vampiricbloodlinesInitial}{VB}

\newcommand{\vampiricbloodlinesintroduction}{%
	The Vampire Covenant army may choose to represent a single Vampiric Bloodline. In this case, all Vampire Counts and Vampire Courtiers in such a Bloodline Army \textbf{must} take the upgrade that corresponds to that Bloodline. All rules associated with a Vampire are only applied to the model part that takes the upgrade and do not apply to any mounts unless specifically stated otherwise.%
}

\newcommand{\ancientbloodpower}{Ancient Blood Power}
\newcommand{\ancientbloodpowerdef}{%
	Bloodline Vampire Counts can take the Ancient Blood Power of their Bloodline instead of taking a Blood Power. All Ancient Blood Powers are \zerotoXperarmy{1}.%
}

\newcommand{\bloodties}{Blood Ties}
\newcommand{\bloodtiesdef}{%
	Certain unit entries in this Army Book include the term Blood Ties, followed by the name of a Bloodline in brackets. If the army includes at least one Vampire Count or Vampire Courtier matching the Bloodline written in brackets in a unit entry, this unit gains access to the associated Blood Ties option.
}

\newcommand{\pathaccess}{The Vampire's Path access is replaced with}

\newcommand{\brotherhoodofthedragon}{Brotherhood of the Dragon}
\newcommand{\brotherhoodofthedragonbloodline}{Brotherhood of the Dragon Bloodline}
\newcommand{\brotherhoodofthedragonbloodlinedef}{%
	The Vampire gains +2 Offensive Skill, \textbf{\pa}, \textbf{\weaponmaster}, and can take any number
of Close Combat Weapons. Whenever possible, unless another model does so first:%
	\begin{itemize}%
		\item The Vampire \textbf{must} accept a Duel.
		\item The Vampire \textbf{must} issue a Duel.
	\end{itemize}%
	Vampire Courtiers cannot be upgraded to Wizard Adepts. Vampire Counts cannot be upgraded to Wizard Masters.%
}
\newcommand{\crimsonrage}{Crimson Rage}
\newcommand{\crimsonragedef}{%
	Every unsaved wound caused by the Vampire's Close Combat Attacks, before applying Multiple Wounds, generates another Close Combat Attack:
	\begin{itemize}
		\item Allocate and resolve the new attacks before removing any casualties, in the same Initiative Step as the attacks that generated them.
		\item You cannot generate more attacks than there were Health Points in the Health Pool towards which the initial attacks were allocated.
		\item The new attacks do not generate any further attacks.
	\end{itemize}
}

\newcommand{\vonkarnstein}{Von Karnstein}
\newcommand{\vonkarnsteinbloodline}{Von Karnstein Bloodline}
\newcommand{\vonkarnsteinbloodlinedef}{%
	The Vampire \textbf{must} reroll failed Vampiric rolls, and the presence of one or more Von Karnstein Vampires grants +1 to their side's Combat Score in any combat which they are Engaged in. Models in the same unit as a Von Karnstein Vampire gain \textbf{\autonomous{}}. If applicable, the ranges of Commanding Presence and Rally Around the Flag of Von Karnstein Vampires are increased by \distance{6}.%
}
\newcommand{\stormcaller}{Storm Caller}
\newcommand{\stormcallerdef}{%
	All units within \distance{12} of the Vampire gain \textbf{\hardtarget{} (1)}.%
}

\newcommand{\lamia}{Lamia}
\newcommand{\lamiabloodline}{Lamia Bloodline}
\newcommand{\lamiabloodlinedef}{%
	The Vampire gains \textbf{\lightningreflexes{}} and suffers \minuss{}1 Attack Value. Enemy units in base contact with one or more Lamia Vampires suffer \minuss{}1 Agility. If the Vampire is not equipped with \ha{} and/or a \shield{}, it gains \textbf{\distracting{}}. Duels issued by the Vampire \textbf{must} (if possible) be accepted by a Character unless a Champion accepts first. Enemy model parts without Harnessed in a Duel with the Vampire suffer \minuss{}1 Attack Value.%
}
\newcommand{\commandment}{Commandment}
\newcommand{\commandmentdef}{%
	The Defensive Skill and Offensive Skill of \rnf{} models in a unit joined by the Vampire are \textbf{set} to 6.%
}


\newcommand{\strigoi}{Strigoi}
\newcommand{\strigoibloodline}{Strigoi Bloodline}
\newcommand{\strigoibloodlinedef}{%
	The Vampire gains \textbf{\fortitude{} (4+)}, \textbf{\hatred{}}, and +1 Health Point, cannot take a mount except
for a \shriekinghorror{}, and may not be equipped with any kind of armour. Vampire Courtiers cannot be upgraded to Wizard Adepts. Vampire Counts cannot be upgraded to Wizard Masters.%
}
\newcommand{\ghoullord}{Ghoul Lord}
\newcommand{\ghoullorddef}{%
	The Vampire, its mount, and all \rnf{} models in its unit gain \textbf{\poisonattacks{}}. If the unit it joins already had \poisonattacks{}, all \rnf{} models in the unit wound automatically on a successful natural to-hit roll of 1 less than normal (i.e. 5+ instead of 6+).%
}

\newcommand{\nosferatu}{Nosferatu}
\newcommand{\nosferatubloodline}{Nosferatu Bloodline}
\newcommand{\nosferatubloodlinedef}{%
	The Vampire suffers \minuss{}1 Attack Value, \minuss{}2 Offensive Skill, and may not be equipped with \ha{} and/or a \shield{}. The Vampire gains \textbf{\awaken{} (\skeletons{}, \zombies{})} and \textbf{\gatesofthenetherworld{}}. A Vampire Courtier \textbf{must} be upgraded to Wizard Apprentice, Wizard Adept, or Wizard Master. A Vampire Count \textbf{must} be upgraded to Wizard Adept or Wizard Master. The Vampire always knows the Hereditary Spell in addition to its other spells.%
}
\newcommand{\bloodmagic}{Blood Magic}
\newcommand{\bloodmagicdef}{%
	During Spell Selection, choose a Path (this may be a different Path than the one the model selects its spells from). When the Vampire or a friendly Wizard within \distance{12} casts the Hereditary Spell or any spell from the chosen Path, the Casting Value of the Spell is reduced by 2, and when rolling casting rolls with a single Magic Dice, a natural roll of \result{1} or \result{2} on the Magic Dice is always a failed Casting Attempt, regardless of any modifiers. When the Vampire or a friendly Wizard within \distance{12} Miscasts, it suffers a +1 Miscast Modifier.
}
