%%%% Unit entries names

% CHARACTERS

\newcommand{\asklanderchief}{\AA{}sklander Chief}

\newcommand{\seidhkennar}{Seidhkennar}


% MOUNTS

\newcommand{\blackstallion}{Black Stallion}

\newcommand{\darkchariot}{Dark Chariot}
\newcommand{\blacksteed}{Black Steed}

\newcommand{\wardais}{War Dais}

\newcommand{\shadowchaser}{Shadow Chaser}

\newcommand{\chimera}{Chimera}

\newcommand{\wastelandbehemoth}{Wasteland Behemoth}


% CORE

\newcommand{\asklanders}{\AA{}sklanders}
\newcommand{\asklander}{\AA{}sklander}

\newcommand{\warhounds}{Warhounds}
\newcommand{\warhound}{Warhound}


% SPECIAL

\newcommand{\warrior}{Warrior}
\newcommand{\warriors}{Warriors}

\newcommand{\asklanderflayers}{\AA{}sklander Flayers}
\newcommand{\asklanderflayer}{\AA{}sklander Flayer}

\newcommand{\asklanderhorsemen}{\AA{}sklander Horsemen}
\newcommand{\asklanderhorseman}{\AA{}sklander Horseman}

\newcommand{\trolls}{Trolls}
\newcommand{\troll}{Troll}

\newcommand{\wargs}{Wargs}
\newcommand{\warg}{Warg}

\newcommand{\huskarls}{Huskarls}
\newcommand{\huskarl}{Huskarl}

\newcommand{\berserkers}{Berserkers}
\newcommand{\berserker}{Berserker}


% LEGENDARY BEASTS

\newcommand{\kraken}{Kraken}

\newcommand{\maraudinggiant}{Marauding Giant}

\newcommand{\joetunn}{J\"otunn}


%%%% Unit entries rules

%% CHARACTERS

% Asklander Chief

\newcommand{\deedsnotwords}{Deeds not Words}
\newcommand{\deedsnotwordsdef}{%
	The model part gains \textbf{\battlefocus} and \textbf{\hatred} when joined to one or more \rnf{} models with \battlefever{}.%
}

\newcommand{\jarl}{Jarl}
\newcommand{\jarldef}{%
	The \AA{}sklander Chief gains +2 Attack Value and may take Special Items for an additional 50 pts.%
}

\newcommand{\allowanceifgeneral}{If General}

\newcommand{\longshipraid}{Longship Raid}
\newcommand{\longshipraiddef}{%
	The model gains \textbf{\ambush{}}. During step 8 of the Pre-Game Sequence, nominate a unit of \AA{}sklanders, Huskarls, or Berserkers that includes no more than 30 models if \AA{}sklanders and no more than 20 models if Huskarls or Berserkers. This unit gains \textbf{\ambush{}}, and the model with Longship Raid \textbf{must} either be deployed or Ambush in this unit. Units using Longship Raid do not roll for Ambush but automatically enter the Battlefield in the second Player Turn. All units using Longship Raid \textbf{must} arrive from the same Board Edge. Otherwise follow the rules for Ambush.%
}

\newcommand{\berserkersbearpeltchiefoptionnote}{Infantry only, see \hyperlink{ASK4berserkers}{\berserkers{}}}

%% MOUNTS

% Dark Chariot
\newcommand{\chassis}{Chassis}

% Chimera
\newcommand{\wings}{Wings}
\newcommand{\wingsdef}{%
	The model's March Rate is \textbf{set} to \distance{16} and  it gains \textbf{\fly{8}{16}} and \textbf{\lighttroops{}}.%
}

% Wasteland Behemoth
\newcommand{\additionallimbs}{Additional Limbs}
\newcommand{\additionallimbsdef}{%
	The model's March Rate is \textbf{set} to \distance{20} and its Armour  is \textbf{set} to 3.%
}


%% CORE

% Warhounds
\newcommand{\releasethehounds}{Release the Hounds}
\newcommand{\releasethehoundsdef}{%
	One use only. May be activated at the start of a friendly Player Turn (all models in a unit \textbf{must} activate this rule at the same time). The model gains \distance{+6} March Rate and \textbf{\devastatingcharge{+1 \At{}, +1 \St{}}} during this Player Turn.%
}


%% SPECIAL

% Warriors
\newcommand{\hellforgedarmour}{Hell-Forged Armour}
\newcommand{\hellforgedarmourdef}{%
	Follows the rules for \pa{} (can be enchanted as if it was \pa{}). The wearer's model gains \textbf{\aegis{} (5+, against Toxic Attacks)}.%
}
\newcommand{\spikedshield}{Spiked Shield}
\newcommand{\spikedshielddef}{%
	\itemrestriction{Models on foot only.}
	Follows the rules for Shields (can be enchanted as if it was a Shield). For each \textbf{successful} Armour Save roll of \textbf{4+} made by the bearer against a Melee Attack while using a Spiked Shield, the model that caused the wound immediately suffers 1 hit with the bearer's \Strength{} and \ArmourPenetration{}, before any casualties are removed, distributed onto the model's Health Pool. This is considered a Special Attack.%
}
\newcommand{\pathofthefavoured}{Path of the Favoured}
\newcommand{\pathofthefavoureddef}{%
	Units with more than half of their models with Path of the Favoured \textbf{must} reroll failed Break Tests. In addition, model parts with Path of the Favoured upgraded to a Champion additionally gain +1 Health Point to a maximum of 3, and their Discipline is \textbf{set} to 9.%
}

% Flayers
\newcommand{\skinninglash}{Skinning Lash}
\newcommand{\skinninglashdef}{%
	A unit with at least one model with Skinning Lash can make a Sweeping Attack against a single unengaged enemy unit when passing within \distance{1} (it does not need to and cannot move through or over that unit). The enemy unit suffers 1 hit with Strength 4 and Armour Penetration 0 for each model with Skinning Lash in the unit. A unit that loses one or more Health Points due to the Skinning Lash Sweeping Attack suffers \minuss{}1 Discipline until the end of its next Player Turn.%
}

% Berserkers
\newcommand{\berserkersbearpelt}{Berserker's Bear Pelt}
\newcommand{\berserkersbearpeltdef}{%
	Follows the rules for \la{} (can be enchanted as if it was \la{}). The bearer gains \textbf{Swiftstride} and \textbf{Unstable}.\newline
	In addition, at the start of any of your Player Turns, all models with Berserker's Bear Pelt in a unit may choose to lose their Shield and gain \textbf{+1 Strength}, \textbf{\battlefocus{}}, \textbf{\fearless{}}, \textbf{\frenzy{}}, and \textbf{\lightningreflexes{}}. The effects last for the remainder of the game.%
}

% Trolls
\newcommand{\icetroll}{Ice Troll}
\newcommand{\icetrolldef}{%
	The model's Armour is \textbf{set} to 2. Flaming Attacks \textbf{must} reroll successful to-wound rolls against the model.%
}
\newcommand{\stupid}{Stupid}
\newcommand{\stupiddef}{%
	At the start of each friendly Player Turn, each unengaged non-Fleeing unit with one or more models with Stupid \textbf{must} take a Discipline Test. If the test is failed, all models in the unit become Shaken until the end of the Player Turn, and in the Movement Phase, directly after Rallying Fleeing units, the unit \textbf{must} move \distance{D6} directly forwards, stopping \distance{1} before Impassable Terrain or other units.%
}
\newcommand{\trollbelch}{Troll Belch}
\newcommand{\trollbelchdef}{%
	At the model part's Initiative Step, the owner may choose an enemy unit Engaged in Combat that the model part is able to attack with Close Combat Attacks. If so, this unit suffers a hit, which is resolved with Strength 5 and Armour Penetration 10, and the model part with Troll Belch may not perform any Close Combat Attacks.%
}


%% LEGENDARY BEASTS

% Marauding Giant
\newcommand{\giantseegiantdo}{Giant See, Giant Do}
\newcommand{\giantseegiantdodef}{The model gains \textbf{\battlefever{}}.}

\newcommand{\rage}{Rage}
\newcommand{\ragedef}{%
	Whenever the model loses a Health Point, it gains +1 Attack Value. Whenever it gains a Health Point, it suffers \minuss{}1 Attack Value.%
}

\newcommand{\monstrousfamiliar}{Monstrous Familiar}
\newcommand{\monstrousfamiliardef}{%
	The model gains \textbf{\wizardapprentice{}}. Instead of selecting spells as normal, it \textbf{must} select one of the following spells (during Spell Selection): \spellformat{\thaumaturgyspellfour}{\thaumaturgy}, \spellformat{\witchcraftspellone}{\witchcraft}, or \spellformat{\frostbite}{\hereditaryspell}.%
}

\newcommand{\giantclub}{Giant Club}
\newcommand{\giantclubdef}{Attacks with a \giantclub{} gain +1 Strength and +1 Armour Penetration.}

\newcommand{\tribalwarspear}{Tribal Warspear}
\newcommand{\tribalwarspeardef}{%
	Attacks with a \tribalwarspear{} gain +1 Strength and \textbf{Multiple Wounds (D3, against Towering Presence)}. Charging enemy units in base contact with the wielder suffer \minuss{}1 Agility. The wielder follows the rules for War Platforms with the following exception: it can only join Infantry units that include at least one \rnf{} \AA{}sklander or Huskarl model.%
}

\newcommand{\bigbrother}{Big Brother}
\newcommand{\bigbrotherdef}{%
	The model's Health Points are \textbf{set} to 8, and its base size is changed to 75\timess{}100 \si{\milli\meter}. The roll for the number of hits from its Stomp Attacks is subject to Maximised Roll.%
}

% Jötunn
\newcommand{\freezingmist}{Freezing Mist}
\newcommand{\freezingmistdef}{%
	Flaming Attacks \textbf{must} reroll successful to-wound rolls against the model.\newline
	All enemy units in base contact with one or more Jötunns suffer:%
	\begin{itemize}%
		\item \minuss{}3 Agility%
		\item \minuss{}1 Armour%
		\item \minuss{}1 Armour Penetration%
	\end{itemize}%
}
