
\newcommand{\specialequipmentintro}{Special Items in this section can only be taken by models with \infernalbrand{}.}

% Special Equipment Names

\newcommand{\onyxcore}{Onyx Core}
\newcommand{\flameoftheeast}{Flame of the East}
\newcommand{\triplespeed}{Triple Speed}

\newcommand{\maskofages}{Mask of Ages}
\newcommand{\kadimbinding}{Kadim Binding}
\newcommand{\blazeofprotection}{Blaze of Protection}

\newcommand{\trialofashuruk}{Trial of Ashuruk}
\newcommand{\prideofzalamantekash}{Pride of Zalaman Tekash}

\newcommand{\goldenidolofshamut}{Golden Idol of Shamut}
\newcommand{\tabletofvezodinezh}{Tablet of Vezodinezh}
\newcommand{\gauntletsofmadzhab}{Gauntlets of Madzhab}
\newcommand{\lugarsdice}{Lugar's Dice}
\newcommand{\breathofthebrassbull}{Breath of the Brass Bull}
\newcommand{\unflame}{Unflame}
\newcommand{\ringofdesiccation}{Ring of Desiccation}

% Special Equipment Texts

\newcommand{\onyxcoredef}{%
	Attacks made with this weapon gain \textbf{\kadimmanifestation{}} and \textbf{Multiple Wounds (D3, against Flammable)}.%
}
\newcommand{\flameoftheeastdef}{%
	The wielder gains \textbf{\volcanicembrace{} (2D3)}. If it already had Volcanic Embrace (X), increase X by 2D3 instead. These 2D3 Grind Attacks are resolved even if the model performed Impact Hits during the same Round of Combat.%
}
\newcommand{\triplespeeddef}{%
	This weapon's Shots are \textbf{set} to 3, and the wielder gains +3 Attack Value while using it. Close Combat Attacks and Shooting Attacks made with this weapon can \textbf{never} hit on worse than 3+.%
}

\newcommand{\maskofagesdef}{%
 The bearer's model gains \textbf{\whispersofthemask{}} (see \hyperlink{ID4immortals}{Immortals} unit). If the bearer's model is Infantry, it also gains +1 Armour.%
}
\newcommand{\kadimbindingrestriction}{Cannot be taken by models with Towering Presence}
\newcommand{\kadimbindingdef}{%
	The bearer's weapons lose \twohanded{} if they had it. While using this Shield, the bearer gains \textbf{\aegis{} (+1, against Flaming Attacks, \maxi{} 2+)} and \textbf{\parry{}}.%
}
\newcommand{\blazeofprotectionrestriction}{Infantry models only}
\newcommand{\blazeofprotectiondef}{%
	While using this Shield, the bearer gains +1 Armour and \textbf{\fearless{}}. Every enemy model in base contact with the bearer that could allocate one or more Close Combat Attacks towards it but doesn't, after resolving its Close Combat Attacks, suffers 1 hit with Strength 4, Armour Penetration 0, and \textbf{\flamingattacks{}}, distributed onto the model's Health Pool. This is considered a Special Attack.%
}

\newcommand{\trialofashurukdef}{%
	The bearer's unit and any unit in base contact with the bearer's unit gain \textbf{\magicresistance{} (2)} that is also applied to friendly spells. This Magic Resistance value cannot be increased.%
}
\newcommand{\prideofzalamantekashrestriction}{Cannot be taken by units that count towards Core}
\newcommand{\prideofzalamantekashdef}{%
	One use only. May be activated at the end of a friendly Movement Phase. Place an 8\timess{}\distance{1} Wall on the Battlefield, with the following conditions and restrictions:%
	\begin{smallitemizeitem}%
		\item One of the Wall's long edges must be aligned and in contact with the Front Facing of the bearer's unit.%
		\item The centre of one of the Wall's long edges must be in contact with the centre of the Front Facing of the bearer's unit.%
		\item The Wall cannot be placed within \distance{1} of any other unit nor any other Terrain Feature except Open Terrain.%
		\item If the Wall cannot be placed in a legal position, the Banner Enchantment cannot be activated.%
	\end{smallitemizeitem}%
}

\newcommand{\goldenidolofshamutdef}{%
	The bearer always has at least Advance Rate \distance{4} and March Rate \distance{12}. In addition, the bearer can cast \spellformat{\alchemyspellthree}{\alchemy} as a Bound Spell with Power Level (4/8).%
}
\newcommand{\tabletofvezodinezhdef}{%
	When the bearer attempts to cast a non-Bound Spell using three or more Magic Dice, treat a single rolled \result{1} as a \result{3}. If the bearer would suffer a Witchfire Miscast effect, treat it as Magical Inferno instead.%
}
\newcommand{\gauntletsofmadzhabrestriction}{Infantry models only}
\newcommand{\gauntletsofmadzhabdef}{%
	The bearer gains +1 Strength and +1 Armour Penetration. Each of its Close Combat Attacks with a natural to-hit roll of \result{1} is distributed onto the bearer's unit (the owner distributes the hits). These hits can only be distributed onto the bearer's model if it is a single model unit.%
}
\newcommand{\lugarsdicedef}{%
 A single model part of the bearer's model can reroll a single failed to-hit, to-wound, or Armour Save roll per Player Turn.%
}
\newcommand{\breathofthebrassbullrestriction}{Cannot be taken by models with Towering Presence}
\newcommand{\breathofthebrassbulldef}{%
	The bearer's model gains +1 Health Point and the bearer gains \textbf{\breathattack{} (\toxicattacks{})}.%
}
\newcommand{\unflamedef}{%
	One use only. May be activated at the start of any Round of Combat. A single enemy unit in base contact with the bearer's model suffers \minuss{}3 Agility, and all attacks against the enemy unit lose \flamingattacks{}. The effects last until the start of the next Player Turn.%
}
\newcommand{\ringofdesiccationdef}{%
	At the start of every Round of Combat, every enemy unit in base contact with the bearer's model gains one instance of \textbf{\incendiary{}}.%
}
