
% Categories

\newcommand{\instrumentsofdestruction}{Instruments of Destruction}
\newcommand{\instrumentsofdestructioninitials}{IoD}

% Hereditary Spell

\newcommand{\furyofnezibkesh}{Fury of Nezibkesh}
\newcommand{\furyofnezibkeshdef}{%
	Place a counter on the target point. At the end of each subsequent Magic Phase, roll a D6. If 1--3 is rolled, add another counter on the same point. If 4--6 is rolled, each unit within 2D6+\distance{X}, where X is equal to the number of counters, must take a Dangerous Terrain (1) Test. Models with Flammable must take a Dangerous Terrain (2) Test instead. The hits from failing this test are Flaming Attacks. If a unit fails a Panic Test forced by the spell, it Flees directly away from the marked point. The spell then ends: remove all counters.%
}

\newcommand{\furyofnezibkeshrestriction}{%
	This spell can only be cast by models with \infernalbrand{}.%
}

% QRS

\newcommand{\blunderbussqrsrule}{Reroll \result{1} to-hit at Short Range}
\newcommand{\rocketbatterymisfire}{Misfires on two \result{1}}
\newcommand{\triplespeedqrsrule}{Never hits on worse than 3+}
\newcommand{\oilflaskthrowerqrseffect}{One \incendiary{} per successful hit}

\newcommand{\shootingmodelrules}{Shooting Model Rules}

\newcommand{\oilskinsqrsrule}{If chosen: \St{} 1, \minuss{}\distance{6} range, one or more hit $\rightarrow$ target gains \incendiary{}}
\newcommand{\clustermunitionsqrsrule}{One or more hits on target $\rightarrow$ D3+1 hits Str 4 AP 1 on the next closest unengaged enemy unit within \distance{6} of target}
\newcommand{\ethercloudqrsrule}{Panic Tests at \minuss{}1 Dis, one or more hits on a unit with Channel $\rightarrow$ the owner loses 1 Veil Token}
\newcommand{\kadimmanifestationqrsrule}{Flaming Attacks, Magical Attacks; Divine Attacks if Flaming Attacks \timess{}2}

\newcommand{\aimtableintro}{%
	The aim of all models equipped with Shooting Weapons is 4+, with the following exceptions:%
}

