%%%% Unit entries names

% CHARACTERS

\newcommand{\makhargyula}{Makhar Gyula}

\newcommand{\enaree}{Enaree}


% MOUNTS

\newcommand{\blackstallion}{Black Stallion}

\newcommand{\blacksteed}{Black Steed}

\newcommand{\darkchariot}{Dark Chariot}

\newcommand{\wardais}{War Dais}

\newcommand{\shadowchaser}{Shadow Chaser}

\newcommand{\chimera}{Chimera}

\newcommand{\wastelandbehemoth}{Wasteland Behemoth}

\newcommand{\greatelk}{Great Elk}


% CORE

\newcommand{\tamyirvassals}{Tamyir Vassals}
\newcommand{\tamyirvassal}{Tamyir Vassal}

\newcommand{\steppewolfhounds}{Steppe Wolfhounds}
\newcommand{\steppewolfhound}{Steppe Wolfhound}

\newcommand{\horsearchers}{Horse Archers}
\newcommand{\horsearcher}{Horse Archer}

\newcommand{\makharlancers}{Makhar Lancers}
\newcommand{\makharlancer}{Makhar Lancer}


% SPECIAL

\newcommand{\makharflayers}{Makhar Flayers}
\newcommand{\makharflayer}{Makhar Flayer}

\newcommand{\warriorknights}{Warrior Knights}
\newcommand{\warriorknight}{Warrior Knight}

\newcommand{\makharchariot}{Makhar Chariot}
\newcommand{\makharcrew}{Makhar Crew}

\newcommand{\turul}{Turul}

\newcommand{\karkadanherd}{Karkadan Herd}
\newcommand{\karkadan}{Karkadan}

\newcommand{\nomadicgiant}{Nomadic Giant}

\newcommand{\steppemammoth}{Steppe Mammoth}



%%%% Unit entries rules

%% CHARACTERS

% Makhar Gyula

\newcommand{\deedsnotwords}{Deeds not Words}
\newcommand{\deedsnotwordsdef}{The model part gains \textbf{\battlefocus} and \textbf{\hatred} when joined to one or more \rnf{} models with \makharbattlefever{}.}

\newcommand{\lightgyula}{\feignedflight{}, \lighttroops{}, and \vanguard{}}
\newcommand{\standardcavalryonly}{Standard Cavalry only}

\newcommand{\Ifgeneral}{If General}
\newcommand{\generalonly}{General only}

\newcommand{\stallionstempest}{Stallion's Tempest}
\newcommand{\stallionstempestdef}{%
	The Makhar Gyula gains +1 Attack Value and may take Special Items for an additional 50 pts. Model parts with Makhar Battle Fever and without Harnessed in a unit that contains Stallion's Tempest gain \textbf{Battle Focus}.%
}

\newcommand{\maresshelter}{Mare's Shelter}
\newcommand{\maresshelterdef}{%
	The Makhar Gyula gains +1 Attack Value and may take Special Items for an additional 50 pts. The model's Commanding Presence range is increased by \distance{6}.%
}

%% MOUNTS

% Dark Chariot

\newcommand{\chassis}{Chassis}

% Chimera

\newcommand{\wings}{Wings}
\newcommand{\wingsdef}{The model's March Rate is \textbf{set} to \distance{16} and it gains \textbf{\fly{8}{16}} and \textbf{\lighttroops{}}.}

% Wasteland Behemoth

\newcommand{\additionallimbs}{Additional Limbs}
\newcommand{\additionallimbsdef}{The model's March Rate is \textbf{set} to \distance{20} and its Armour is \textbf{set} to 3.}


%% CORE

% Tamyir Vassals

\newcommand{\bowcategorynote}{A unit with Bows also counts towards Raining Death.}

% Horse Archers

\newcommand{\rider}{Rider}
\newcommand{\horse}{Horse}

% Makhar Lancers

\newcommand{\recurvebowcategorynote}{A unit with Recurve Bows also counts towards Raining Death.}


%% SPECIAL

% Warrior Knights

\newcommand{\hellforgedarmour}{Hell-Forged Armour}
\newcommand{\hellforgedarmourdef}{%
	Follows the rules for \pa{} (can be enchanted as if it was \pa{}). The wearer's model gains \textbf{\aegis{} (5+, against Toxic Attacks)}.%
}

\newcommand{\pathofthefavoured}{Path of the Favoured}
\newcommand{\pathofthefavoureddef}{%
	Units with more than half of their models with Path of the Favoured \textbf{must} reroll failed Break Tests. In addition, model parts with Path of the Favoured upgraded to a Champion additionally gain +1 Health Point to a maximum of 3, and their Discipline is \textbf{set} to 9.%
}

% Makhar Chariot

\newcommand{\crewandriderchoice}{Crew and Riders \textbf{must} both choose the same of either}

% Turul

\newcommand{\territorialhunter}{Territorial Hunter}
\newcommand{\territorialhunterdef}{%
	The model gains \textbf{\ambush{}}. In addition, when declaring if the model will Ambush (during step 8 of the Pre-Game Sequence), you may declare that the model Ambushes from an Impassable Terrain Feature instead of the Board Edge. If so, follow the rules for Ambush but replace all instances of \enquote{Board Edge} in the rules for Ambush with \enquote{edge of any Impassable Terrain}.%
}

% Flayers

\newcommand{\boworrecurvebowcategorynote}{A unit with Bows or Recurve Bows also counts towards Raining Death.}
\newcommand{\skinninglash}{Skinning Lash}
\newcommand{\skinninglashdef}{%
	A unit with at least one model with Skinning Lash can make a Sweeping Attack against a single unengaged enemy unit when passing within \distance{1} (it does not need to and cannot move through or over that unit). The enemy unit suffers 1 hit with Strength 4 and Armour Penetration 0 for each model with Skinning Lash in the unit. A unit that loses one or more Health Points due to one or more Skinning Lash Sweeping Attacks suffers \minuss{}1 Discipline until the end of its next Player Turn.%
}

\newcommand{\beasttaker}{Beast Taker}
\newcommand{\beasttakerdef}{%
Close Combat Attacks and Shooting Attacks from Short Range made by the rider gain \textbf{\lethalstrike{} (against Beasts and Cavalry)}.
}

% Karkadan Herd

\newcommand{\followtheherd}{Follow The Herd}
\newcommand{\followtheherddef}{%
	The unit can never benefits from Commanding Presence or Rally Around the Flag. The unit gains +1 Discipline for each Full Rank.%
}
\newcommand{\stampede}{Stam\-pe\-de}
\newcommand{\stampededef}{%
	If the model's unit has at least one Full Rank, the model's Impact Hits cause an additional D3 hits for each model in the same file behind it (normally 2D3/3D3/etc. instead of D3).%
}

% Nomadic Giant

\newcommand{\nomadicgiantcategorynote}{%
	A unit with a \textbf{Giant Recurve Bow} also counts towards Raining Death.%
}

\newcommand{\giantrecurvebow}{Giant Recurve Bow}

\newcommand{\giantseegiantdo}{Giant See, Giant Do}
\newcommand{\giantseegiantdodef}{The model gains \textbf{\makharbattlefever{}}.}

\newcommand{\rage}{Rage}
\newcommand{\ragedef}{%
	Whenever the model loses a Health Point, it gains +1 Attack Value. Whenever it gains a Health Point, it suffers \minuss{}1 Attack Value.%
}

\newcommand{\giantclub}{Giant Club}
\newcommand{\giantclubdef}{Attacks with a \giantclub{} gain +1 Strength and +1 Armour Penetration.}

\newcommand{\tribalwarspear}{Tribal Warspear}
\newcommand{\tribalwarspeardef}{%
	Attacks with a \tribalwarspear{} gain +1 Strength and \textbf{Multiple Wounds (D3, against Towering Presence)}. Charging enemy units in base contact with the wielder suffer \minuss{}1 Agility. The wielder follows the rules for War Platforms with the following exception: it can only join Infantry units that include at least one \rnf{} Barbarian Infantry model.%
}

\newcommand{\bigbrother}{Big Brother}
\newcommand{\bigbrotherdef}{%
	The model's Health Points are \textbf{set} to 8, and its base size is changed to 75\timess{}100 \si{\milli\meter}. The roll for the number of hits from its Stomp Attacks is subject to Maximised Roll.%
}

%%% RAINING DEATH

% Steppe Mammoth

\newcommand{\crew}{Crew}

\newcommand{\onthesteppemammoth}{on the \steppemammoth}
\newcommand{\fistofthemakhar}{Fist of the Makhar}

\newcommand{\steppemammothnote}{A model can buy this upgrade even if the army already has a Battle Standard Bearer.}

