% Army Model Rules Names

% Aegis already defined

\newcommand{\theenemywithin}{The Enemy Within}

\newcommand{\nobodyexpects}{Nobody Expects\dots}

\newcommand{\pledgedtodarkness}{Pledged to Darkness}

\newcommand{\sacrificialofferings}{Sacrificial Offerings}

\newcommand{\daemonicsummon}{Daemonic Summon}


% Army Model Rules Texts

\newcommand{\aegisdef}{%
	Unit profiles in this Army Book contain an additional Characteristic, which corresponds to the units' Aegis Saves, shortened \Aeg{}. This Characteristic is treated as if the unit has the Personal Protection Aegis (X+) written on their profile, where X is the \Aeg{} Characteristic value. Not having an \Aeg{} value does not prevent a unit from being the target of an Aegis modifier.%
}

\newcommand{\theenemywithindef}{%
	An army from the Cultists Army Book gains a +6 modifier to the roll for choosing the Deployment Zone.%
}

\newcommand{\nobodyexpectsdef}{%
	At the start of step 7 of the Pre-Game Sequence (Select Spells), the opponent may choose one of their Characters to be the Inquisitor. The Inquisitor gains \textbf{\fear{}}, \textbf{\hatred{}} and \textbf{\terror{}}. All models with Pledged to Darkness gain \textbf{\battlefocus{}} against the Inquisitor.%
}

\newcommand{\waywardchildren}{Wayward Children}
\newcommand{\fallenheroes}{Fallen Heroes}
\newcommand{\thedishonoured}{The Dishonoured}
\newcommand{\kinslayers}{Kinslayers}
\newcommand{\speciesarchetype}{Species Archetype}

\newcommand{\pledgedtodarknessdef}{%
	Models with Pledged to Darkness can only join or be joined by models with Pledged to Darkness. While joined by one or more Characters, \rnf{} models with Pledged to Darkness gain \textbf{Fearless}.\DTLpar%
	Certain units with Pledged to Darkness can choose one of the following 4 Species Archetypes, which give the models the changes stated below. If any unit chooses one of these Species Archetypes, all units capable of doing so \textbf{must} choose the same Species Archetype.\DTLpar%
	\pledgedtodarknesstable%
}

\newcommand{\basesetto}{\newrule{\basesize{} \textbf{set} to}}
\newcommand{\resiliencesetto}{\Resilience{} \textbf{set} to}
\newcommand{\marchratesetto}{\MarchRate{} \textbf{set} to}
\newcommand{\thedishonourednote}{Daemon Symbiotes and Possessed have their March Rate \textbf{set} to \distance{12} instead.}

\newcommand{\sacrificialofferingsdef}{%
	Immediately before performing a Casting Attempt with a Wizard in a unit containing one or more models with Sacrificial Offerings, you may inflict 1 hit against that unit. This hit wounds automatically with Armour Penetration 10 and with no saves of any kind allowed. If a Health Point loss was caused against a model with Sacrificial Offerings, the Casting Attempt gains a +1 Casting Modifier. Each unit can be affected by Sacrificial Offerings only once per Magic Phase.%
}

\newcommand{\daemonicsummondef}{%
	During Siphon the Veil, each non-Fleeing model with Daemonic Summon may perform a single Daemonic Summon:
	\begin{enumerate}
	\item Choose a unit from the Summoned Daemons Army Category on your Army List.
	\item Discard a number of Veil Tokens from your Veil Token pool corresponding to the chosen unit's Point Cost divided by 200, rounding fractions up. During the owner's Player Turn 1, only 2 Veil Tokens may be discarded for Daemonic Summon. Otherwise, a maximum of 6 Veil Tokens may be discarded for Daemonic Summon per Player Turn.
	\item The chosen unit is deployed in a legal formation fully within \distance{12} of the model that performs the Summon. All models must be placed at least \distance{1} away from other units and from Impassable Terrain. If the whole unit cannot be deployed, then no models can be deployed.
	\end{enumerate}
	The unit counts as as having moved for Moving and Shooting. Any unit that entered the Battlefield on Game Turn 4 or later loses Scoring.%
}