
% Special Equipment Names

\newcommand{\lifeforcetalisman}{Lifeforce Talisman}

\newcommand{\ledgerofsouls}{Ledger of Souls}

\newcommand{\scurryingveil}{Scurrying Veil}

\newcommand{\locket}{Locket of Sunna}

\newcommand{\gemoffaithstithe}{Gem of Faith's Tithe}

\newcommand{\fiendishsnares}{Fiendish Snares}

% Special Equipment Texts

\newcommand{\lifeforcetalismandef}{%
	Whenever the bearer Miscasts, you may inflict D3 hits on the bearer's unit. These hits wound automatically with Armour Penetration 10 and with no saves of any kind allowed. If so, the owner may choose to modify the Miscast with either a +1 or a \minuss{}1 modifier.%
}

\newcommand{\ledgerofsoulsdef}{%
	Immediately before removing a friendly model without Insignificant in a unit within \distance{9} of the bearer's model due to enemy attacks, you gain one Veil Token for each Health Point that model had the first time it entered the Battlefield.%
}

\newcommand{\scurryingveildef}{%
	The bearer gains \textbf{Tiny}, and its March Rate is \textbf{set} to \distance{20}.%
	\tinylayout{\tinyrule}{\ruletype{\universalrule}\tinyruledef}%
}
\newcommand{\tinyrule}{Tiny}
\newcommand{\tinyruledef}{%
	The model ignores friendly units when moving in the Charge and Movement Phase, but must follow the Unit Spacing rule at the end of the move.%
}
\newcommand{\scurryingveilrestriction}{Standard Height models only}

\newcommand{\locketdef}{%
	When fighting a Duel, choose a single model part with neither Harnessed nor Inanimate that the bearer is fighting with. The bearer and the chosen model part \textbf{must} swap their Characteristic values of Strength, Armour Penetration, Resilience, Agility, and Attack Value. This is done before applying other modifiers. If the chosen model part does not have a Defensive Profile of its own, use the combined model's Defensive Profile instead.%
}

\newcommand{\gemoffaithstithedef}{%
	Whenever the bearer casts a spell, the owner may choose a friendly Champion with Pledged to Darkness within \distance{12}. If so, use the position of the Champion when drawing Line of Sight and measuring range. For Direct spells, also use the Champion's Front Arc. The owner must use all of these or none at all. If the spell is successfully cast, the Champion suffers 1 hit that wounds automatically with Armour Penetration 10 with no saves of any kind allowed.%
}

\newcommand{\fiendishsnaresdef}{%
	Immediately after Deployment Zones are chosen, the owner nominates a Terrain Feature with its centre in their half of the Battlefield. Unless that Terrain Feature is Impassable Terrain or Open Terrain, it becomes Dangerous Terrain (2).%
}
