\maintitle{KoEchangelog}{\changelog}


\subtitle{0.205.2}

\begin{itemize}
\item Logotype on the titlepage changed for our new logotype.
\item Area Attack, updated with the reverted order of X and Y.
\item Bug with the spacing around headers corrected.
\end{itemize}

\subtitle{0.205.1}

\begin{itemize}
\item Forest guide, rewording.
\item Wyrmwood Core, rewording.
\item Brigands, Hard Target (1) and Light Troops were forgotten in last update.
\end{itemize}

\subtitle{0.205.0}

\begin{itemize}
\item Blue and green colours from 0.204 removed.
\item Standardisation of the formatting of lists.
\item Confusion between hyphen (-), en-dash (--), em-dash (---) and minus symbol (−) corrected.
\item \enquote{x} replaced with \enquote{\timess{}} as the mathematical times symbol (for example in 25\timess{}50).
\item Replace Hard Target with Hard Target (1), Last one Turn with One Turn, Catapult(X) with Catapult (X\timess{}X).
\item Beta for the Quick Reference Sheet, check it and give us feedback!
\end{itemize}

Un-nesting rulebook model rules. Models given rules that used to be nested in other rules.
\begin{itemize}[label={-}]
\item Light Troops and Swiftstride no longer part of Fly.
\item Fearless no longer part of Frenzy.
\item Hard Target and Light Troops no longer part of Skirmisher.
\item Fear no longer part of Terror.
\item Fearless no longer part of Unbreakable, Unstable, or Supernal.
\item Move or Fire no longer part of War Machine.
\item Not a Leader no longer part of War Platforms.
\end{itemize}

\subtitle{Army Model Rules}

\begin{itemize}[label={-}]
\item Blessing, do not affect enemy models
\item Breath of the Lady, now work for all melee attacks.
\end{itemize}

%\subtitle{Oaths}
%
%\begin{itemize}[label={-}]
%\item Introduction, rewording.
%\end{itemize}

\subtitle{Special Equipment}

\begin{itemize}[label={-}]
\item Banner of Roland, only work against charges declared by the unit.
\item Faith of Percival, only work when using the shield.
\end{itemize}

\subtitle{Characters}

\begin{itemize}[label={-}]
\item Equitan Unicorn, removed duplicate model rule.
\end{itemize}

%\subtitle{Core}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Special}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Queen's Bows}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Naval Ordnance}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Ancient Allies}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

\subtitle{Points}

\begin{itemize}[label={-}]
\item Virtue of Valour 60
\item Virtue of Audacity 50
\item Tristan´s Resolve 55
\item Crystal of the valiant charge 30
\item Wyrmwood core 45
\item Castellan heavy armour 0
- throwing weapons 5
\item Peasant Bowmen start 170
\item Paesant cruders start 150
\item Sacred reliquary 150
\item Scorpion 120
\end{itemize}
