
\addtocontents{toc}{\protect\columnbreak}
\part{Psychology}
\label{psychology}

\section{Panic Test}
\label{panic_test}

Panic Tests are Discipline Tests that units have to take immediately after any of the following situations arise:

\begin{itemize}[label={-}]
\item A friendly unit is destroyed within \distance{6} of the unit (including Fleeing off the Table).
\item A friendly unit Breaks from combat within \distance{6} of the unit.
\item A friendly unit Flees through the unit.
\item In a single phase, the unit suffers Health Point losses equal to or greater than \SI{25}{\percent} of the number of Health Points that it had at the start of the phase. This does not apply to single model units that started the game as a single model (i.e. with a starting number of 1 model on the Army List).
\end{itemize}

Units which fail a Panic Test Flee directly away from the closest enemy unit (Centre of Unit to Centre of Unit). If there are no enemy units on the Battlefield, randomise the direction.

If the Panic Test was forced by any of the cases listed below, the unit Flees directly away from the enemy unit that caused the Panic Test (Centre of Unit to Centre of Unit).
\begin{itemize}[label={-}]
\item A spell cast by an enemy model.
\item A Model Rule on an enemy model (such as \hyperref[terror]{Terror}).
\item Losing \SI{25}{\percent} or more Health Points, and the final wounds causing the Health Point losses to reach or go above \SI{25}{\percent} were due to an attack by an enemy unit.
\end{itemize}

Units do not take Panic Tests if they are Engaged in Combat, if they are already Fleeing or if they already passed a Panic Test during this Phase.

\section{Shaken}
\label{shaken}

A Shaken model cannot perform any of the following actions:

\begin{itemize}[label={-}]
\item Declare Charges;
\item Pursuit;
\item \hyperref[overrun]{Overrun};
\item Advance Move;
\item March Move;
\item Reform (it can Combat Reform and Post-Combat Reform);
\item \hyperref[random_movement]{Random Movement} move;
\item Shooting Attacks.
\end{itemize}

\newpage
\section{Fleeing}
\label{fleeing}

When a unit is Fleeing, it cannot perform any voluntary actions (a voluntary action is an action that a unit would have the option to not perform). This includes (but is not limited to):

\begin{itemize}[label={-}]
\item Declare Charges;
\item Charge Reactions (other than Flee);
\item Move in any way other than a Flee Move;
\item Shoot;
\item \hyperref[channel]{Channelling};
\item Cast spells or activate One use only Special Equipment which need to be activated voluntarily.
\end{itemize}

Models cannot receive \hyperref[commanding_presence]{Commanding Presence} or \hyperref[rally_around_the_flag]{Rally Around the Flag} from a Fleeing model.