\part{Command Group}
\label{command_group}

Certain units feature the option of upgrading regular models to Champion, Musician, or Standard Bearer. These models are known as the Command Group.

\section{Musician}
\label{musician}

A Musician gains \hyperref[front_rank]{\textbf{Front Rank}} and \hyperref[stand_behind]{\textbf{Stand Behind}}.

\subsubsection{Swift Reform}
\label{swift_reform}

During the Movement Phase, a unit with a Musician may execute a Swift Reform instead of a \hyperref[reform]{Reform}. The unit makes a Reform with the following exceptions:
\begin{itemize}[label={-}]
\item The unit is not prohibited from shooting in the next Shooting Phase.
\item The unit can perform an \hyperref[advance_move]{Advance Move} after the Reform. For the purpose of no model being able to end its movement with its centre further away than its Advance Rate from its starting position, measure this distance after the Reform.
\item No model can end its movement (after an Advance Move) with its centre further away than its March Rate from its starting position (before the Reform).
\end{itemize}

\subsubsection{March to the Beat}
\label{march_to_the_beat}

March Tests taken by units within \distance{8} of one or more enemy units with a Musician are taken at -1 Discipline, unless the unit that wishes to March also has a Musician.

\section{Standard Bearer}
\label{standard_bearer}

A Standard Bearer gains \hyperref[front_rank]{\textbf{Front Rank}} and \hyperref[stand_behind]{\textbf{Stand Behind}}.

\subsubsection{Combat Bonus}

A side with Standard Bearers adds +1 to its Combat Score for each Standard Bearer.

\section{Champion}
\label{champion}

A Champion gains \hyperref[front_rank]{\textbf{Front Rank}}.

\subsubsection{First Among Equals}
\label{first_among_equals}

A Champion gains +1 Attack Value. If it is a multipart model, the Characteristics increase only affects a single model part, which must be a model part without \hyperref[harnessed]{Harnessed} or \hyperref[inanimate]{Inanimate}.

\subsubsection{Ordering the Charge}
\label{ordering_the_charge}

When a unit with a Champion rolls for their Charge Range, they \textbf{always} count as rolling at least a \result{4}. If the charge is still failed, ignore this rule and use the rolled dice to determine the Failed Charge Move.

\section{Removing Casualties}

If a Musician or Standard Bearer is to be removed as a casualty, replace another \rnf{} model (if there is any) with the Musician or Standard Bearer - it is assumed that another soldier picked up their tool and responsibility. Champions are however not easily replaced and can be specifically targeted in some situations (e.g. by allocating Close Combat Attacks, attacks that target individual models such as attacks from \hyperref[focused]{Focused} spells, or attacks that target all models in a unit). If enough Health Points are lost from a unit's Health Pool to remove all \rnf{} models from the unit as casualties, any remaining Health Points lost are distributed \rewordedrule{on}to the Champion, even if it is fighting in a Duel.
