\part{Special Equipment}
\label{special_equipment}

\section{Special Equipment Categories}

All Special Equipment belongs to one of the following categories:

\begin{itemize}[label={-}]
\item Weapon Enchantments
\item Armour Enchantments
\item Banner Enchantments
\item Artefacts
\end{itemize}

Each category of Special Equipment is subject to the following rules. Unless stated otherwise, all Special Equipment is \textbf{One of a Kind.}

\subsection{Weapon Enchantments}
\label{weapon_enchantments}

Weapon Enchantments are upgrades to weapons. The upgraded mundane weapon is referred to as enchanted weapon and follows all rules for both the original weapon and the Weapon Enchantment. A model may only have a single Weapon Enchantment. If a model has more than one weapon then it must be noted on the Army List which weapon has been enchanted (remember that all models are equipped with a Hand Weapon). Each Weapon Enchantment applies to specific weapons (e.g. a Great Weapon) or a category of weapons (e.g. a Close Combat Weapon). Note that Shooting Weapons that count as a Close Combat Weapon in Close Combat (such as a Brace of Pistols from the Empire of Sonnstahl Army Book) cannot normally be Enchanted with a Close Combat Weapon enchantment (unless stated otherwise). A model armed with an enchanted weapon (including a Hand Weapon) must use it.

\subsection{Armour Enchantments}
\label{armour_enchantments}

Armour Enchantments are upgrades to armour. The upgraded mundane armour is referred to as enchanted armour and follows all the rules for both the original armour and the Armour Enchantment. Each piece of armour a model is carrying may be given a single Armour Enchantment. If the wearer has more than one piece of armour that could be enchanted, then it must be noted on the Army List which piece of armour has been enchanted. If a model has no armour, it cannot take Armour Enchantments. Each Armour Enchantment applies to specific armour (e.g. Heavy Armour) or a category of armour (e.g. Suit of Armour). 

\subsection{Banner Enchantments}
\label{banner_enchantments}

Banner Enchantments are upgrades to \hyperref[standard_bearer]{Standard Bearers} and \hyperref[bsb]{Battle Standard Bearers}. The upgraded banner is referred to as enchanted banner. Each banner may normally only have one single Banner Enchantment, except for Battle Standard Bearers, who may take up to two Banner Enchantments.

\subsection{Artefacts}
\label{artefacts}

A model may have up to two Artefacts.

\section{Properties of Special Equipment}

\subsection{Dominant}
\label{dominant}

Some Special Equipment is noted as being Dominant. A model may only have a single Dominant Special Equipment.

\subsection{Who is Affected}

Special Equipment often refers to their wielder, wearer, or bearer. These terms mean the same thing and refer to the model part the Special Equipment was bought for, \textbf{excluding its mount}. Other pieces of Special Equipment affect the model, wearer's model, or bearer's model; these terms refer to the entire model, including the mount (note that these terms override the \hyperref[massive_bulk]{Massive Bulk} rules). Finally, a third group of Special Equipment refers to the wearer's unit or bearer's unit; this type of Special Equipment affects all model parts (including mounts) in the same unit as the wearer/bearer of the Artefact (including the wearer/bearer itself).

\subsection{One Use Only}
\label{one_use_only}

These effects can only be used once per game. 

\newpage
\section{List of Common Special Equipment}

The Special Equipment listed below is considered Common Special Equipment and is available to all models and units who have the option to buy Special Equipment from the corresponding category. It is often bought in addition to army-specific Special Equipment.

\subsection{Weapon Enchantments}

\startpricelist
\pricelistitem{Blessed Inscriptions}{65}{%
Close Combat Weapon enchantment.\\
Attacks made with this enchanted weapon gain \hyperref[divine_attacks]{\textbf{Divine Attacks}}, \hyperref[magical_attacks]{\textbf{Magical Attacks}}, and failed to-wound rolls must be rerolled.
}
\pricelistitem{Titanic Might}{65}{%
Close Combat Weapon enchantment.\\
Attacks made with this enchanted weapon gain +3 Strength and \hyperref[magical_attacks]{\textbf{Magical Attacks}}.
}
\pricelistitem{King Slayer}{60}{%
Close Combat Weapon enchantment.\\
The wielder of this enchanted weapon gains +X Strength, +X Armour Penetration, +X Attack Value, and \hyperref[magical_attacks]{\textbf{Magical Attacks}} when attacking with it, where X is equal to the number of enemy Characters in base contact with the wielder's unit. This bonus is calculated and effective at the \hyperref[initiative_order]{Initiative Step} when such attacks are made.
}
\pricelistitem{Hero's Heart}{55}{%
Hand Weapon and Paired Weapons enchantment.\\
The wielder of this enchanted weapon gains +1 Attack Value when using it. Attacks made with this enchanted weapon gain \hyperref[magical_attacks]{\textbf{Magical Attacks}} and \textbf{always} have at least Strength 5 and at least Armour Penetration 3. 
}
\pricelistitem{Shield Breaker}{50}{%
Close Combat Weapon enchantment.\\
Attacks made with this enchanted weapon gain +6 Armour Penetration, \hyperref[magical_attacks]{\textbf{Magical Attacks}}, and can \textbf{never} wound on to-wound rolls better than 3+.
}
\pricelistitem{Touch of Greatness}{45}{%
Close Combat Weapon enchantment.\\
Attacks made with this enchanted weapon gain +1 Strength, +1 Armour Penetration, and \hyperref[magical_attacks]{\textbf{Magical Attacks}}.\\
Strength modifiers from this weapon (combining both mundane and Weapon Enchantment modifiers) cannot exceed +2 (but can exceed +2 through modifiers from other sources, such as spells).
}
\pricelistitem{Supernatural Dexterity}{40}{%
Close Combat Weapon enchantment.\\
The wielder of this enchanted weapon gains +2 Offensive Skill and +2 Agility while using it, and attacks made with it gain \hyperref[magical_attacks]{\textbf{Magical Attacks}}.
}
\pricelistitem{Cleansing Light}{20}{%
Close Combat Weapon enchantment.\\
At the start of each Round of Combat, the wielder may choose to give attacks made with this enchanted weapon \hyperref[flaming_attacks]{\textbf{Flaming Attacks}} and \hyperref[magical_attacks]{\textbf{Magical Attacks}}.
}
\endpricelist
\clearpage

\subsection{Armour Enchantments}

\startpricelist
\pricelistitem{Death Cheater}{95}{%
Suits of Armour enchantment.\\
The wearer gains \hyperref[fortitude]{\textbf{Fortitude (4+)}} and +1 Armour.
}
\pricelistitem{Destiny's Call}{70}{%
\itemrestriction{Standard Size models only.}
Suits of Armour enchantment.\\
The wearer gains \hyperref[aegis]{\textbf{Aegis (4+)}} and its Armour is \textbf{set} to 3 and cannot be improved beyond this.
}
\pricelistitem{Essence of Mithril}{60}{%
\itemrestriction{Standard Size models only.} 
Suits of Armour enchantment.\\
The wearer gains +5 Armour, to a maximum of 5.
}
\pricelistitem{Dusk Forged}{50}{%
Shield enchantment.\\
The bearer may choose to reroll its failed Armour Saves while using this Shield. If it does, it automatically fails all Special Saves.
}
\pricelistitem{Ghostly Guard}{40}{%
Heavy Armour and Plate Armour enchantment.\\
The wearer gains +2 Armour against non-\hyperref[magical_attacks]{Magical Attacks}.
}
\pricelistitem{Basalt Infusion}{35}{%
Suits of Armour enchantment.\\
The wearer gains +1 Armour and \textbf{\hyperref[aegis]{Aegis} (3+, against \hyperref[flaming_attacks]{Flaming Attacks})}. The wearer automatically fails all \hyperref[fortitude]{Fortitude} Saves.
}
\pricelistitem{Alchemist's Alloy}{15}{%
Suits of Armour enchantment.\\
The wearer gains +1 Armour and suffers -2 Offensive Skill.
}
\pricelistitem{Willow's Ward}{15}{%
\itemrestriction{Models on foot only.}
Shield enchantment.\\
While using this Shield, the bearer cannot use \hyperref[parry]{Parry}, gains +1 Armour, and \hyperref[impact_hits]{Impact Hits} distributed \rewordedrule{onto} the bearer suffer -2 Armour Penetration.
}
\endpricelist

\clearpage
\subsection{Banner Enchantments}

\startpricelist

\pricelistitem{Banner of Speed}{50}{%
\itemrestriction{0-3 per Army.}
A unit with one or more Banners of Speed gains +1 Advance Rate and +2 March Rate.
}
\pricelistitem{Rending Banner}{45}{%
\itemrestriction{0-3 per Army.}
One use only. May be activated at the start of a Round of Combat. Close Combat Attacks from \rnf{} models in the bearer's unit gain +1 Armour Penetration until they are no longer Engaged in Combat. A model can only be affected by a single Rending Banner at the same time.
}
\pricelistitem{Stalker's Standard}{45}{%
\itemrestriction{0-3 per Army.}
The bearer's unit gains \hyperref[strider]{\textbf{Strider}}.
}
\pricelistitem{Banner of Discipline}{35}{%
\itemrestriction{0-3 per Army.}
The bearer's unit may reroll failed \hyperref[panic_test]{Panic Tests}. If the \hyperref[bsb]{Battle Standard Bearer} or the General is part of the bearer's unit, it automatically passes all its Panic Tests instead.
}
\pricelistitem{Banner of the Relentless Company}{35}{%
\itemrestriction{0-3 per Army.}
One use only. May be activated during the controlling player's Movement Phase. All Infantry models in the bearer's unit \textbf{always} have March Rate \distance{15}, until the end of the Player Turn. Only a single Banner of the Relentless Company may be activated during the same Phase.
}
\columnbreak
\pricelistitem{Flaming Standard}{35}{%
\itemrestriction{0-3 per Army.}
One use only. May be activated at the start of a Round of Combat or before shooting with the bearer's unit. The bearer's unit gains \hyperref[flaming_attacks]{\textbf{Flaming Attacks}}. If activated when Engaged in Combat, effects lasts until the bearer's unit is no longer Engaged in Combat. If activated before Shooting with the bearer's unit, this effect lasts until the end of the phase.
}
\pricelistitem{Aether Icon}{25}{%
\itemrestriction{0-3 per Army.}
The bearer's unit gains \hyperref[magic_resistance]{\textbf{Magic Resistance (1)}}. If the unit already had Magic Resistance, it instead increases the Magic Resistance value by 1.
}
\pricelistitem{Legion Standard}{25}{%
\itemrestriction{0-3 per Army.}
A unit with one Legion Standard increases the maximum of its Rank Bonus by +1 (normally this means the unit can add up to 4 Full Ranks to its Combat Score). A unit with two Legion Standards increases the maximum of its Rank Bonus by +2 instead.
}
\endpricelist
\clearpage

\subsection{Artefacts}

\startpricelist
\pricelistitem{Crown of Autocracy}{70}{%
The bearer gains +1 Discipline. If taken by the General, the opponent is awarded an additional +200 Victory Points if the bearer is removed as a casualty.
}
\pricelistitem{Book of Arcane Mastery}{60}{%
\itemrestriction{Dominant. Wizard Apprentices and Adepts only.}
The bearer's first Casting Attempt in each Magic Phase gains +2 to cast. When using a single Magic Dice for this Casting Attempt, a natural roll of \result{1} or \result{2} on the Magic Dice is always a failed Casting Attempt, regardless of any modifiers.
}
\pricelistitem{Binding Scroll}{55}{%
\itemrestriction{0-2 per Army.}
One use only. May be activated after Siphon the Veil (at the end of step 3 of the Magic Phase Sequence). When activated, pick an enemy model and select one of its Attribute, Bound, or Learned Spells. The selected model cannot cast the chosen instance of the spell during this Magic Phase. Only a single Binding Scroll may be activated during the same phase.
}
\pricelistitem{Crown of the Wizard King}{55}{%
\itemrestriction{Cannot be taken by Wizards.}
During \hyperref[spell_selection]{Spell Selection}, randomise a Magic Path (from all Paths in The \nth{9} Age: Fantasy Battles - Paths of Magic). The bearer is a \hyperref[wizard_apprentice]{\textbf{Wizard Apprentice}} using the randomised Path. It cannot select the \hyperref[hereditary_spells]{Hereditary Spell}.
}
\pricelistitem{Essence of a Free Mind}{55}{%
\itemrestriction{Dominant. Wizards only.}
The bearer may choose up to two Paths on its Army List instead of one (from the ones normally available to it). During \hyperref[spell_selection]{Spell Selection}, choose which one of the two Paths to use.
}
\pricelistitem{Rod of Battle}{55}{%
The bearer can cast a \hyperref[bound_spells]{Bound Spell}, Power Level (4/8):\\
Type: Augment. Range \distance{12}. Duration: Lasts One Turn.\\
The target gains +1 to hit with its Close Combat Attacks.
}
\pricelistitem{Crystal Ball}{50}{%
After \hyperref[spell_selection]{Spell Selection} (at the end of step 7 of the Pre-Game Sequence), mark a single enemy model on the opponent's Army List. All Dispelling Attempts of spells cast by that model gain a +1 Dispelling Modifier, provided the bearer is on the Battlefield.
}
\pricelistitem{Talisman of Shielding}{50}{%
The bearer gains \hyperref[aegis]{\textbf{Aegis (5+)}}.
}
\pricelistitem{Talisman of the Void}{50}{%
The bearer gains \hyperref[channel]{\textbf{Channel (1)}}. 
}
\pricelistitem{Lightning Vambraces}{45}{%
The bearer can cast a \hyperref[bound_spells]{Bound Spell}, Power Level (4/8):\\
Type: Hex, Missile, Damage. Range \distance{24}. Duration: Instant. The target suffers 2D6 hits with Strength 3, Armour Penetration 0, and \hyperref[magical_attacks]{\textbf{Magical Attacks}}.
}
\pricelistitem{Magical Heirloom}{45}{%
\itemrestriction{Dominant. Wizards only.}
The bearer knows the \hyperref[hereditary_spells]{Hereditary Spell} in addition to its other spells. 
}
\pricelistitem{Ranger's Boots}{45}{%
\itemrestriction{Standard Size models on foot only.}
The bearer gains \hyperref[strider]{\textbf{Strider}} and, unless using \hyperref[fly]{Flying Movement}, +2 Advance Rate up to a maximum of 10, and +4 March Rate up to a maximum of 20.
}
\pricelistitem{Obsidian Rock}{40}{%
The bearer gains \hyperref[magic_resistance]{\textbf{Magic Resistance (2)}}.
}
\pricelistitem{Sceptre of Power}{40}{%
\itemrestriction{Dominant.}
One use only. A Wizard with this Artefact may add a single Magic Dice from its Magic Dice pool to one of its casting rolls or dispelling rolls, after seeing the casting or dispelling roll (note that casting rolls cannot exceed the limit of max 5 Magic Dice).
}
\pricelistitem{Dragon Staff}{30}{%
The bearer gains \hyperref[breath_attack]{Breath Attack} (Strength 3, Armour Penetration 0, \hyperref[flaming_attacks]{Flaming Attacks}).
}
\pricelistitem{Dragonfire Gem}{20}{%
The bearer gains \textbf{\hyperref[aegis]{Aegis} (2+, against \hyperref[flaming_attacks]{Flaming Attacks})}. The bearer automatically fails all \hyperref[fortitude]{Fortitude} Saves.
}
\pricelistitem{Potion of Strength}{20}{%
\itemrestriction{Cannot be taken by models with \hyperref[towering_presence]{Towering Presence}.}
One use only. May be activated at the start of any phase or Round of Combat. Until the end of the Player Turn the bearer gains \hyperref[crush_attack]{\textbf{Crush Attack}}.
}
\pricelistitem{Lucky Charm}{10}{%
One use only. May be activated when the bearer's model fails an Armour Save. This failed Armour Save may be rerolled.
}
\pricelistitem{Potion of Swiftness}{10}{%
One use only. May be activated at the start of any Phase or Round of Combat. Until the end of the Player Turn, the bearer gains +3 Agility.
}
\endpricelist
