
%%UNIT NAMES
%% CHARACTERS
\newcommand{\marshal}{Marshal}

\newcommand{\kncdr}{Knight Commander}

\newcommand{\prelate}{Prelate}

\newcommand{\eoswizard}{Wizard}

\newcommand{\artificer}{Artificer}

\newcommand{\inquisitor}{Inquisitor}

%% MOUNTS
\newcommand{\pegasus}{Pegasus}

\newcommand{\horse}{Horse}

\newcommand{\younggriff}{Young Griffon}

\newcommand{\greatgriff}{Great Griffon}

\newcommand{\dragon}{Dragon}

\newcommand{\arcengine}{Arcane Engine}
\newcommand{\chassis}{Chassis}
\newcommand{\crew}{Crew}

\newcommand{\altbattle}{Altar of Battle}

%% CORE
\newcommand{\hvyinf}{Heavy Infantry}

\newcommand{\ltinf}{Light Infantry}

\newcommand{\statemilitia}{State Militia}

\newcommand{\eleccav}{Electoral Cavalry}
\newcommand{\knight}{Knight}

%% SPECIAL
\newcommand{\impguard}{Imperial Guard}

\newcommand{\knsun}{Knights of the Sun Griffon}
\newcommand{\knsunQRS}{Kn of the Sun Griffon}

%% IMP AUX
\newcommand{\imprgr}{Imperial Ranger}

\newcommand{\reiters}{Reiters}
\newcommand{\reiter}{Reiter}

%% IMP ARM
\newcommand{\arty}{Artillery}

%%SUNNA FURY
\newcommand{\flagellants}{Flagellants}
\newcommand{\flagellant}{Flagellant}

\newcommand{\stank}{Steam Tank}
\newcommand{\steelram}{Steel Ram}

%% UNIT RULES ENTRIES
% CHARACTERS
% MARSHAL
\newcommand{\greattac}{Great Tactician}
\newcommand{\greattacdef}{%
A Great Tactician may give two Orders per turn instead of one.
}

\newcommand{\impprince}{Imperial Prince}
\newcommand{\impprincedef}{%
The model part gains +1 Attack Value, and is equipped with a Hand Weapon enchanted with The Light of Sonnstahl. An Imperial Prince may only take up to 50 pts of Special Items.
}

%KNIGHT CDR
\newcommand{\firstkn}{First Knight}
\newcommand{\firstkndef}{%
When the model is joined to a unit of Knightly Orders, the unit gains \textbf{Fearless}, and if the model is the General, the \rnf{} models in the unit also gain \textbf{Parent Unit}.
}

\newcommand{\musttakeoneofthefollowingbfNOC}{\textbf{Must} take one of the following:}
\newcommand{\seemount}{see mount}

%ARTIFICER
\newcommand{\mstart}{Master Artificer}
\newcommand{\mstartdef}{%
The Master Artificer may give the Order \textbf{Ready! Aim! Fire!} to a Parent Unit or Support Unit it has joined.
}

%INQ
\newcommand{\blessedsteel}{Blessed Steel}
\newcommand{\blessedsteeldef}{%
The model part gains +2 Agility. Close Combat Attacks made by the model part gain +1 Strength and +1 Armour Penetration.
}

\newcommand{\blesssteelcountsas}{Models with \textbf{Silver Shots} additionally count towards \impaux{}.}

\newcommand{\silvershot}{Silver Shots}
\newcommand{\silvershotdef}{%
The attack gains \textbf{Multiple Wounds (D3)}, \textbf{Lethal Strike}, and must reroll failed to-wound rolls.
}

% MOUNTS
%ALT BATTLE
\newcommand{\holyrelic}{Holy Relic}
\newcommand{\holyrelicdef}{%
Friendly units within \distance{6} of the bearer gain \textbf{Hatred}. Model parts with Harnessed are not affected. All Blessings Bound Spells cast by the rider have Type: Aura and Range \distance{6} (replace Type: Caster’s Unit). The model can cast \textit{Unerring Strike} from Divination as a Bound Spell with Power Level (4/8).
}

%ARCANE ENGINE
\newcommand{\arcanesh}{Arcane Shield}
\newcommand{\arcaneshdef}{%
Friendly units within \distance{6} of the model gain \textbf{Distracting}. The Arcane Engine can cast \textit{Perception of Strength} from Cosmology as a Bound Spell with Power Level (4/8).
}

\newcommand{\foresight}{Foresight}
\newcommand{\foresightdef}{%
Friendly units within \distance{6} of the model gain \textbf{Lightning Reflexes}. The Arcane Engine can cast \textit{Ice and Fire} from Cosmology as a Bound Spell with Power Level (4/8).
}

% CORE
% LT INF
\newcommand{\reserves}{Reserves}
\newcommand{\reservesdef}{%
The unit is treated as \textbf{Insignificant} by Parent and Support Units.
}

\newcommand{\irregulars}{Irregulars}
\newcommand{\irregularsdef}{%
The model gains \textbf{\lighttroops{}}, \textbf{\skirmisher{}} and \textbf{\hardtarget{} (1)}.
}

%ELEC CAV
\newcommand{\knorders}{Knightly Orders}
\newcommand{\knordersdef}{%
The Knight gains +1 Offensive Skill, +1 Defensive Skill, +1 Strength, and +1 Armour Penetration. Knightly Orders cannot take Great Weapons.
}

\newcommand{\knorderupgrade}{A single unit (or if the army includes a\newline\kncdr{}, \textbf{any} unit) may be upgraded to\newline\textbf{\knorders{}}}

% SPECIAL

% IMP AUX
%IMP RANGERS
\newcommand{\frontiersmen}{Frontiersmen}
\newcommand{\frontiersmendef}{%
The model automatically passes Panic Tests caused by Terror.
}

\newcommand{\beasthunters}{Beast Hunters}
\newcommand{\beasthuntersdef}{%
When using a Bow, the Shooting Attack gains \textbf{Lethal Strike (against Beast)} and Shots 2.
}

%REITERS
\newcommand{\fireimpact}{Fire on Impact!}
\newcommand{\fireimpactdef}{%
A Charging model part with Fire on Impact! using a Pistol, a Brace of Pistols, or a Repeater Pistol \textbf{always} strikes at Initiative Step 10, and has the Strength of its Close Combat Attacks \textbf{set} to 4 and their Armour Penetration \textbf{set} to 2 (regardless of the user's Agility, Strength, and Armour Penetration).
}

\newcommand{\replacepstwithonechoice}{\optionschoice{Replace its \pistol{} with \onechoiceonlyNOC{}:}}

% IMP ARM
% BLACK POWDER ARTY
% CANNON
\newcommand{\cannondef}{%
This Shooting Weapon can be fired in two ways:%
\begin{itemize}
\item As a \textbf{\cannon{}} Artillery Weapon with \range{72}, \shots{1}, \St{} 4 [10], \AP{} 0 [10], \textbf{\areaattack{1\timess{}5}}, [\textbf{\multiplewounds{D3+1, \clippedwings{}}{}}].
\item As an Artillery Weapon with \range{12}, \shots{2D6}, \St{} 4, \AP{} 4.
\end{itemize}
}

% VOLLEY GUN
\newcommand{\impvolleygun}{Volley Gun}
\newcommand{\impvolleygundef}{\range{24}, \shots{3D6*2}, \St{} 5, \AP{} 3.
}

% MORTAR
\newcommand{\impmortar}{Mortar}
\newcommand{\impmortardef}{%
\textbf{\catapult{6\timess{}6}} with \range{12--48}, \shots{1}, \St{} 3 [6], \AP{} 1 [4], [\textbf{\multiplewounds{D3}{}}].
}

% ROCKETEER
\newcommand{\improcket}{Imperial Rocketeer}
\newcommand{\improcketdef}{%
\textbf{\catapult{1\timess{}1}} with \range{15--48}, \shots{3}, \St{} 5, \AP{} 3, \textbf{\multiplewounds{D3}{}}, This weapon treats all results on the Misfire Table as Malfunction (each shot can cause a Misfire).
}

%SUNNA FURY
%FLAGELLANTS
\newcommand{\fanatical}{Fanatical}
\newcommand{\fanaticaldef}{%
When a model with Fanatical is killed by a Melee Attack during any Initiative Step of a Round of Combat it is fighting, remove it as a casualty only at the end of Initiative Step 0.
}

\newcommand{\zealots}{Zealots}
\newcommand{\zealotsdef}{%
Prelates may join this unit and gain \textbf{Unbreakable} and \textbf{Fearless} while in the unit.
}

%STANK
\newcommand{\stankcannon}{Steam Cannon}
\newcommand{\stankcannondef}{%
\textbf{\cannon{}} with \range{36}, \shots{1}, \St{} 3 [7], \AP{} 0 [6], \textbf{\areaattack{1\timess{}5}}, [\textbf{\multiplewounds{D3, \clippedwings{}}{}}].
}

\newcommand{\steampowered}{Steam Powered}
\newcommand{\steampowereddef}{%
The model may choose not to move despite having Random Movement, and its Pursuit and Overrun Distance is \textbf{always} \distance{0}.\newline
Before moving in the Movement Phase, the model may choose to replace its Random Movement (4D3) with Random Movement (5D3) until the end of the Movement Phase. If so, the Steam Cannon cannot be used during this Player Turn.
}