
\maintitle{DLchangelog}{\changelog}

\subtitle{2.2.2}

\begin{itemize}
\item Blazing Glories, changed to singular.
\item Threshing Engine, Draft Beasts and Tillers, changed to singular.
\item Unnatural Roots, rewording.
\item Divining Snout, clarification.
\item Dominion of Lust, rewording.
\item Red Haze, clarification.
\item Mirrored Scales, clarification.
\item Spell Craving, clarification about multiple instances of a spell.
\end{itemize}

\subtitle{2.2.1}

Removal of blue text and slight layout adjustments.

\subtitle{2.2}

\subtitle{Clarification and Corrections}

\begin{itemize}
\item Mark of the Eternal Champion, rewording, we don't need to say it affects only the Champion when given to a unit any more. Imps, Mark of the Eternal Champion only affects the Champion now.
\item Sorcerous Antennae, rewording to clarify the interaction with the Rune of Harnessing.
\end{itemize}

\subtitle{Rules changes}

\begin{itemize}
\item Iron Husk, now sets the Resilience to 6, and can be taken by Gigantic models.
\item Tarskin, reworked. Attacks towards the bearer hits the attacker when the roll to hit is a \result{1}, with a Guiding version. Renamed: Mirrored Scales.
\item Unnatural Roots, reworked. Gives +1 Combat Score (for one or more instances).
\item Brimstone Secretions, Guiding version now only affects \rnf{} in the bearer's unit, not in a \distance{6} range any more.
\item Third Eye, reworked. Now allows to draw the Flux Card at the beginning of the Charge Phase for better planning.
\item Piercing Spike, doesn't give +1 Strength any more, but now works against any value of Armour.
\item Bronze Backbone, rules replaced with Hatred.
\item Greenfire Eyes, now can and must be activated when the unit fails its first Charge Range roll.
\item Broodmother, reworked. Can now be taken by Gigantic models. Now Raises D3 HPs in the unit when the model (or the \rnf{} models in the unit for Guiding) caused at least 3 HP losses.
\item Divining Snout, effect for only one Special Item removed.
\item Grasping Proboscis, modified to activate in a same way as Broodmother, gives D3 Veil Tokens
\item Mesmerising Plumage, reworked. Enemy units in base contact suffers \minuss{}1 Off and Def (for one or more instances).
\item Chilling Yawn, \minuss{}3 \baddown{} \minuss{}2 Agility.
\item Red Haze, not limited to one Round of Combat any more. Works only for Close Combat Attacks.
\item Incendiary Ichor, now has a Guiding version, makes automatically fail all Fortitude Saves.
\item Vanadra's Scourge, \fly{6}{16} $\rightarrow$ \fly{7}{14}, Off 8 \goodup{} 9, Path of Dal Magoth removed, Wizard Master option, removed, Magic Paths: Evocation and Thaumaturgy.
\item Eidolons, option to Scout.
\item Threshing Engine, Horde and Legion upgrades now count as Gigantic for the purpose of determining the number of Full Ranks. No more 0--3 restriction for Mark of the Eternal Champion on the Standard Threshing Engine.
\item Blazing Glories, Adv \distance{7} \goodup{} \distance{8}, Mar \distance{14} \goodup{} \distance{16} (same for Fly), now counts as a Character for the purpose of Duels, and gains Stubborn while in Duel.
\item Bloat Flies:
\begin{itemize}
\item \fly{7}{14} \baddown{} \fly{6}{12}
\item Def 2 \goodup{} 3
\item Aegis 6+ \goodup{} 5+
\item Att 3 \goodup{} 4
\item AP 3 \baddown{} 2
\item Acid Blood, 2 Toxic Attacks \baddown{} 1 Toxic Attack, works only when a Fortitude Test is failed
\item Unnatural Roots replaced with Dextrous Tentacles
\item Option for Musician added
\item Broodmother can no longer be taken with another Manifestation
\end{itemize}
\end{itemize}

\subtitle{Balance changes}

\begin{itemize}
\item incoming.
\item Manifestations of Father Chaos:
\begin{itemize}
\item Tarskin: Standard 75 \costdown{} 45, Guiding 70
\item Iron Husk 85 \costup{} 110
\item Brimstone Secretions: Standard 30 \costdown{} 25, Guiding 55 \costdown{} 35
\item Unnatural Roots 35 \costdown{} 25
\end{itemize}
\item Manifestations of Envy:
\begin{itemize}
\item Greenfire Eyes 25 \costup{} 40
\item Piercing Spike: Standard 45 \costdown{} 25, Guiding 70 \costdown{} 60
\end{itemize}
\item Manifestations of Gluttony:
\begin{itemize}
\item Broodmother: Standard 40 \costup{} 60, Guiding 70 \costup{} 80
\end{itemize}
\item Manifestations of Greed:
\begin{itemize}
\item Divining Snout: Standard 25 \costdown{} 15, Guiding 35 \costdown{} 30
\item Grasping Proboscis: Standard 10 \costup{} 20, Guiding 15 \costup{} 25
\end{itemize}
\item Manifestations of Pride:
\begin{itemize}
\item Bronze Backbone: Standard 55 \costdown{} 30, Guiding 85 \costup{} 70
\end{itemize}
\item Manifestations of Sloth:
\begin{itemize}
\item Chilling Yawn 85 \costdown{} 75
\item Segmented Shell: Guiding 40 \costdown{} 35
\end{itemize}
\item Manifestations of Wrath:
\begin{itemize}
\item Red Haze: Standard 45 \costdown{} 40, Guiding 90 \costdown{} 80
\item Incendiary Ichor: Guiding 30
\end{itemize}
\item Omen of Savar, Throne of Overwhelming Splendour 200 \costdown{} 185
\item Kuulima's Deceiver, Fly and Light Troops 45 \costdown{} 40
\item Maw of Akaan, Starting cost 565 \costup{} 570
\item Vanadra's Scourge:
\begin{itemize}
\item Starting cost 705 \costup{} 725
\item Wizard Apprentice 25 \costup{} 40
\item Wizard Adept 85 \costup{} 115
\end{itemize}
\item Harbinger of Father Chaos:
\begin{itemize}
\item Starting Cost 150 \costup{} 160
\item Dark Pulpit 55 \costdown{} 50
\item Burning Wheel 90 \costdown{} 85
\end{itemize}
\item Great Beast of Prophecy, Fly and Light Troops 65 \costdown{} 60
\item Succubi:
\begin{itemize}
\item Starting cost 205 \costup{} 210
\item Additional models 18\permodel{} \costup{} 19\permodel{}
\item Mesmerising Plumage 1\permodel{} \costup{} 2\permodel{}
\end{itemize}
\item Lemures, Unnatural Roots 3 \costdown{} 2
\item Myrmidons:
\begin{itemize}
\item Starting cost 205 \costup{} 215
\item Additional models 20\permodel{} \costup{} 22\permodel{}
\item Piercing Spike 5\permodel{} \costdown{} 4\permodel{}
\end{itemize}
\item Eidolons:
\begin{itemize}
\item Starting cost 200 \costdown{} 185
\item Additional models 37\permodel{} \costdown{} 33\permodel{}
\item Scout 4\permodel{}, \zerotoXunitsperarmy{1}
\end{itemize}
\item Hellhounds:
\begin{itemize}
\item Starting cost 165 \costup{} 170
\item Additional models 16\permodel{} \costup{} 20\permodel{}
\end{itemize}
\item Threshing Engine:
\begin{itemize}
\item Horde Thresher 60 \costup{} 75
\item Legion Thresher 115 \costup{} 140
\item Divining Snout 20 \costdown{} 15
\end{itemize}
\item Titanslayer Chariot:
\begin{itemize}
\item Starting cost 220 \costdown{} 205
\item Divining Snout 20 \costdown{} 15
\end{itemize}
\item Clawed Fiends:
\begin{itemize}
\item Starting cost 275 \costup{} 280
\item Additional models 96\permodel{} \costup{} 97\permodel{}
\item Broodmother 13\permodel{} \costup{} 15\permodel{}
\item Mesmerising Plumage 7\permodel{} \costdown{} 8\permodel{}
\end{itemize}
\item Mageblight Gremlins:
\begin{itemize}
\item Piercing Spike 8\permodel{} \costup{} 9\permodel{}
\item Unnatural Roots 6\permodel{} \costup{} 7\permodel{}
\end{itemize}
\item Hoarders:
\begin{itemize}
\item Divining Snout 7\permodel{} \costdown{} 5\permodel{}
\item Grasping Proboscis 5\permodel{} \costdown{} 3\permodel{}
\end{itemize}
\item Sirens, Mesmerising Plumage 4 \costup{} 5
\item Blazing Glories, starting cost 280 \costup{} 320
\item Hope Harvester, Chilling Yawn 75 \costdown{} 65
\item Brazen Beasts:
\begin{itemize}
\item Starting cost 345 \costup{} 350
\item Additional models 103\permodel{} \costdown{} 102\permodel{}
\item Red Haze 22\permodel{} \costdown{} 21\permodel{}
\item Chitinous Scales 9\permodel{} \costdown{} 8\permodel{}
\end{itemize}
\item Furies, Mesmerising Plumage 2\permodel{} \costup{} 3\permodel{}
\item Veil Serpents:
\begin{itemize}
\item Starting cost 265 \costdown{} 250
\item Additional models 58\permodel{} \costdown{} 55\permodel{}
\end{itemize}
\item Bloat Flies:
\begin{itemize}
\item Starting cost 290 \costup{} 310
\item Broodmother 12\permodel{} \costup{} 15\permodel{}
\item Dextrous Tentacles 7\permodel{}
\end{itemize}
\end{itemize}
