
\newcommand{\daemonicmanifestations}{Daemonic Manifestations}
\newcommand{\daemonicmanifestationsInitial}{DM}

\newcommand{\daemonicmanifestationsintro}{%
Daemon Legions armies possess their own version of Special Items called Daemonic Manifestations. They follow the rules for Special Items, with the exception that they are not \oneofakind{} and that models cannot be affected by more than one instance of each Manifestation, unless specifically stated otherwise.%
}

\newcommand{\guidingmanifestations}{Guiding Manifestations}
\newcommand{\guidingmanifestationsdef}{%
Some Daemonic Manifestations have a Guiding version. These can be taken either as their normal \enquote{non-Guiding} version, or their Guiding version. Unless specifically stated otherwise, the normal version of Manifestations is taken. When using this version, ignore all text \guidingversion{with this colour-coding}.

Only Characters can take Guiding Manifestations. If the Guiding version is taken, this must be noted on your Army List. Follow the rules stated \guidingversion{with this colour-coding} and ignore point costs written in the standard way.

Note that Guiding and non-Guiding Manifestations are considered to be the same Manifestation for the purpose of Duplication Limits.%
}

%%%% Manifestations of Father Chaos
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsoffatherchaos}{Manifestations of Father\newline Chaos}

\newcommand{\dexteroustentacles}{Dextrous Tentacles}
\newcommand{\livingshield}{Living Shield}
\newcommand{\chitinousscales}{Chitinous Scales}
\newcommand{\centipedelegs}{Centipede Legs}
\newcommand{\unnaturalroots}{Unnatural Roots}
\newcommand{\sorcerousantennae}{Sorcerous Antennae}
\newcommand{\markoftheeternalchampion}{Mark of the Eternal Champion}
\newcommand{\chargedtendrils}{Charged Tendrils}
\newcommand{\tarskin}{Tar Skin}
\newcommand{\darkhide}{Dark Hide}
\newcommand{\hammerhand}{Hammer Hand}
\newcommand{\ironhusk}{Iron Husk}
\newcommand{\brimstonesecretions}{Brimstone Secretions}
\newcommand{\thirdeye}{Third Eye}
\newcommand{\clovenhooves}{Cloven Hooves}
\newcommand{\witheringvapour}{Withering Vapour}
\newcommand{\kaleidoscopicflesh}{Kaleidoscopic Flesh}

\newcommand{\dexteroustentaclesdef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains +1 Agility.%
}
\newcommand{\livingshielddef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains \textbf{\parry}.%
}
\newcommand{\chitinousscalesdef}{%
The model gains +2 Armour, to a maximum of 3.%
}
\newcommand{\centipedelegsdef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains +\distance{1} Advance Rate.\newpage% remove \newpage when translating
}
\newcommand{\unnaturalrootsdef}{%
When a unit with one or more instances of this Manifestation rolls a Break Test or Combat Reform test, the Combat Score difference counts as 2 less, to a minimum of 0 (this has no effect on other units Engaged in the same Combat).%
}
\newcommand{\sorcerousantennaedef}{%
\itemrestriction{0--2 per Army.}
During Siphon the Veil in each of your Magic Phases, each unit with one or more instances of this Manifestation adds a Veil Token to your Veil Token pool.
}
\newcommand{\markoftheeternalchampiondef}{%
This Manifestation can only be taken by single model units or units with a Champion.  If given to a unit with a Champion, only the Champion is affected by the Manifestation.\newline
If the affected model is not a Wizard, it gains \textbf{\wizardapprentice} and must select \spellformat{\spearofinfinity}{\hereditaryspell}. If the affected model is already a Wizard, it knows \spellformat{\spearofinfinity}{} in addition to its other spells and cannot select it during Spell Selection.%
}
\newcommand{\chargedtendrilsdef}{%
At the end of Siphon the Veil, the owner may store one additional Veil Token, up to a maximum of 6.%
}
\newcommand{\tarskindef}{%
\itemrestriction{Dominant.}
Enemy units in base contact with one or more models with this Manifestation suffer \minuss{}1 Attack Value.%
}
\newcommand{\darkhidedef}{%
The model gains \textbf{\scout} with the following exception: it must be deployed fully inside the owner's Deployment Zone.%
}
\newcommand{\hammerhanddef}{%
The bearer gains +1 Attack Value.%
}
\newcommand{\ironhuskdef}{%
\itemrestriction{Cannot be taken by Gigantic models.}
The model gains +1 Resilience.%
}
\newcommand{\brimstonesecretionsdef}{%
\itemrestriction{\guidingversion{Dominant}.}
Attacks made against the model \guidingversion{and against \rnf{} models in friendly units within \distance{6} of the model} no longer are \divineattacks{} (if they were).%
}
\newcommand{\thirdeyedef}{%
When a Learned Spell that targets the model or its unit is successfully cast, the bearer may cast that spell as a Bound Spell with Power Level (5/8) in the following Magic Phase.%
}
\newcommand{\clovenhoovesdef}{%
The model gains \textbf{\impacthits{} (D3)}. These Impact Hits are resolved with Strength 5 and Armour Penetration 2.%
}
\newcommand{\witheringvapourdef}{%
\itemrestriction{0--2 per Army.}
The model gains \textbf{\breathattack{\St{} 3, \AP{} 2}}.\columnbreak% remove the columnbreak when translating
}
\newcommand{\kaleidoscopicfleshdef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains \textbf{\hardtarget{} (1)}.%
}


%%%% Manifestations of Envy
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofenvy}{Manifestations of Envy}

\newcommand{\venomsacs}{Venom Sacs}
\newcommand{\greenfireeyes}{Greenfire Eyes}
\newcommand{\piercingspike}{Piercing Spike}

\newcommand{\venomsacsdef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains \textbf{\poisonattacks}. If the model's Close Combat Attacks {or those of \rnf{} models in its unit} already were \poisonattacks{} from another source than this Manifestation, the attack will automatically wound on successful to-hit rolls of 5+, instead of 6+.%
}
\newcommand{\greenfireeyesdef}{%
One use only. May be activated when the model's unit fails a Charge Range roll. If all models in the unit activate their \greenfireeyes{}, the Charge Range roll may be rerolled.%
}
\newcommand{\piercingspikedef}{%
\itemrestriction{\guidingversion{Dominant}.}
Close Combat Attacks against enemy models with an Armour value of 3 or higher made by the model \guidingversion{and each \rnf{} model in its unit} gain +1 Strength.%
}


%%%% Manifestations of Gluttony
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofgluttony}{Manifestations of Gluttony}

\newcommand{\unhingingjaw}{Unhinging Jaw}
\newcommand{\digestivevomit}{Digestive Vomit}
\newcommand{\broodmother}{Broodmother}

\newcommand{\unhingingjawdef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} must reroll failed to-wound rolls from Close Combat Attacks against Large or Gigantic models.%
}
\newcommand{\digestivevomitdef}{%
\itemrestriction{\guidingversion{Dominant}.}
One use only. Must be activated the first time the bearer's unit performs a Post-Combat Pivot or a Post-Combat Reform. The model \guidingversion{and each \rnf{} model in its unit} gains +1 Strength and +1 Armour Penetration until the end of the game.%
}
\newcommand{\broodmotherdef}{%
\itemrestriction{Cannot be taken by Gigantic models. Dominant.}
At the end of each Round of Combat during which the model's unit was Engaged in Combat, roll a D6 and add the number of unsaved wounds caused by Close Combat Attacks from models with \broodmother{} \guidingversion{and \rnf{} model in the bearer's unit}. On a score of 7 or more, the unit Raises D3 Health Points.%
}


%%%% Manifestations of Greed
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofgreed}{Manifestations of Greed}

\newcommand{\graspingproboscis}{Grasping Proboscis}
\newcommand{\diviningsnout}{Divining Stout}
\newcommand{\smotheringcoils}{Smothering Coils}

\newcommand{\graspingproboscisdef}{%
\itemrestriction{\guidingversion{Dominant}.}
At the end of each Round of Combat during which the model's unit was Engaged in Combat, roll a D6 and add the number of unsaved wounds caused by Close Combat Attacks from models with \graspingproboscis{} \guidingversion{and \rnf{} model in the bearer's unit}. On a score of 6 or more, you gain one Veil Token to your Veil Token pool.%
}
\newcommand{\diviningsnoutdef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} must reroll failed Charge Range rolls when rolling for Charge Range against a unit that contains one Special Item. In addition, if the Charged unit contains more than one Special Item, all models with \diviningsnout{} also gain +\distance{2} Advance Rate for the Charge Range roll. The effects only apply if all models in the unit are affected by \diviningsnout{}.%
}
\newcommand{\smotheringcoilsdef}{%
The model \guidingversion{and each \rnf{} model in its unit} gains +1 to-wound with Close Combat Attacks against models with Scoring.%
}


%%%% Manifestations of Lust
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsoflust}{Manifestations of Lust}

\newcommand{\hotblood}{Hot Blood}
\newcommand{\mesmerisingplumage}{Mesmerising Plumage}
\newcommand{\roaminghands}{Roaming Hands}

\newcommand{\hotblooddef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains \textbf{\devastatingcharge{+2 \Ag{}}}.%
}
\newcommand{\mesmerisingplumagedef}{%
\itemrestriction{Dominant.}
Friendly units (including the bearer's unit) Engaged in the same Combat as one or more models with this Manifestation gain +1 Offensive Skill and +1 Defensive Skill while Engaged in that Combat.%
}
\newcommand{\roaminghandsdef}{%
\itemrestriction{\guidingversion{Dominant}.}
When the unit is Engaged with an enemy unit's Flank or Rear Facing, the model \guidingversion{and each \rnf{} model in its unit} gains +1 Strength and +1 Armour Penetration.%
}


%%%% Manifestations of Pride
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofpride}{Manifestations of Pride}

\newcommand{\hornsofhubris}{Horns of Hubris}
\newcommand{\stiffupperlip}{Stiff Upper Lip}
\newcommand{\bronzebackbone}{Bronze Backbone}

\newcommand{\hornsofhubrisdef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains \textbf{\vanguard{} (\distance{6})}.%
}
\newcommand{\stiffupperlipdef}{%
Discipline Tests taken by units with at least one model with this Manifestation are subject to Minimised Roll.%
}
\newcommand{\bronzebackbonedef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains \textbf{\hatred}. If the model's unit loses a Round of Combat, the model \guidingversion{and each \rnf{} model in its unit} must reroll failed to-hit rolls in the following Round of Combat.%
}


%%%% Manifestations of Sloth
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofsloth}{Manifestations of Sloth}

\newcommand{\segmentedshell}{Segmented Shell}
\newcommand{\auraofdespair}{Aura of Despair}
\newcommand{\chillingyawn}{Chilling Yawn}

\newcommand{\segmentedshelldef}{%
\itemrestriction{\guidingversion{Dominant}.}
When the bearer \guidingversion{or a \rnf{} model in its unit} suffers a wound from an attack with \multiplewounds{}{}, the number of wounds that it is multiplied into (due to \multiplewounds{}{}) is reduced by 1, to a minimum of 1.%
}
\newcommand{\auraofdespairdef}{%
\itemrestriction{Dominant.}
Enemy units suffer \minuss{}\distance{2} Advance Rate to a minimum of 1 when rolling for Charge Range against units with at least one model with this Manifestation.%
}
\newcommand{\chillingyawndef}{%
\itemrestriction{Dominant.}
Enemy units in base contact with one or more models with this Manifestation suffer \minuss{}3 Agility.%
}


%%%% Manifestations of Wrath
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofwrath}{Manifestations of Wrath}

\newcommand{\incendiaryichor}{Incendiary Ichor}
\newcommand{\whipcracktail}{Whipcrack Tail}
\newcommand{\redhaze}{Red Haze}

\newcommand{\incendiaryichordef}{%
The model gains \textbf{\aegis{} (2+, against \flamingattacks{})}. All Melee Attacks (including Special Attacks) and Shooting Attacks made by models with \incendiaryichor{} become \textbf{\flamingattacks{}}.%
}
\newcommand{\whipcracktaildef}{%
\itemrestriction{\guidingversion{Dominant}.}
The model \guidingversion{and each \rnf{} model in its unit} gains \textbf{\lightningreflexes{}}.%
}
\newcommand{\redhazedef}{%
\itemrestriction{\guidingversion{Dominant}.}
This Manifestation may be activated at the start of any Round of Combat. All models in the same unit must activate it if one model does. When activated, the model's Close Combat Attacks \guidingversion{and those of \rnf{} models in its unit} gain +1 Strength and +1 Armour Penetration, but each of its attacks with a natural to-hit roll of \result{1} is distributed onto the bearer's unit. The effects last until the end of the Round of Combat.%
}
