\maintitle{UDchangelog}{\changelog}

\subtitle{0.205.2}

\begin{itemize}
\item Logotype on the titlepage changed for our new logotype.
\item Area Attack, updated with the reverted order of X and Y.
\item Bug with the spacing around headers corrected.
\item Dust to Dust, typo.
\item Charnel Catapult, typo.
\end{itemize}

\subtitle{0.205.1}

\begin{itemize}
\item Dread Sphinx, Switfstride removed from profile as it's included in Beast.
\item Petrifying Gaze, reworded.
\end{itemize}

\subtitle{0.205.0}

\begin{itemize}
\item Blue and green from 0.204 removed.
\item Standardisation of the formatting of lists.
\item Confusion between hyphen (-), en-dash (--), em-dash (---) and minus symbol (−) corrected.
\item \enquote{x} replaced with \enquote{\timess{}} as the mathematical times symbol (for example in 25\timess{}50).
\item Replace Hard Target with Hard Target (1), Last one Turn with One Turn, Catapult(X) with Catapult (X\timess{}X).
\item Beta for the Quick Reference Sheet, check it and give us feedback!
\end{itemize}

Un-nesting rulebook model rules. Models given rules that used to be nested in other rules.
\begin{itemize}
\item Light Troops and Swiftstride no longer part of Fly.
\item Fearless no longer part of Frenzy.
\item Hard Target and Light Troops no longer part of Skirmisher.
\item Fear no longer part of Terror.
\item Fearless no longer part of Unbreakable, Unstable, or Supernal.
\item Move or Fire no longer part of War Machine.
\item Not a Leader no longer part of War Platforms.
\end{itemize}
%
%\subtitle{Layout}
%
%\begin{itemize}[label={-}]
%\item Blue and green from 0.204.0 removed. A few formatting issues and typos corrected.
%\item New layout for the Well of Souls Flux Card.
%\end{itemize}
%
%%\subtitle{Background}
%%\begin{itemize}[label={-}]
%%\item 
%%\end{itemize}
%
\subtitle{Model Rules}

\begin{itemize}
\item Terracota, clarification
\end{itemize}

\subtitle{Special Equipment}

\begin{itemize}
\item Crown of the Pharaohs, clarifications
\end{itemize}

\subtitle{Army List and Units}

\begin{itemize}
\item Scarab Swarm Dis 7
\item Well of Souls, clarification and now a separate rule
\end{itemize}

\subtitle{Points}
\begin{itemize}
\item Sacred Hourglass 95
\item Book of the Dead 60
\item Scroll of Desiccation 15
\item Pharaoh - Sha Guardian Mount 365
\item Nomarch - Sha Guardian Mount 360
\item Tomb Harbinger - Amuut Mount 50
\item Tomb Architect - Amuut Mount 40
\item Death Cult Hierarch - Ark of Ages Mount 145
\item Skeleton cavalry start 190
- additional 17
\item Skeleton chariot legion charioteers 15
\item Shabtis archers additional 80
\item Sand Scorpion 160
\item Battle Sphinx 480
\item Dread Sphinx 480
\end{itemize}