
% Army Model Rules Names

\newcommand{\scentofblood}{Scent of Blood}
\newcommand{\fleetcommander}{Fleet Commander}
\newcommand{\beastmaster}{Beast Master}

\newcommand{\killerinstinct}{Killer Instinct}
\newcommand{\deathtrance}{Death Trance}

\newcommand{\krakenshide}{Kraken's Hide}

\newcommand{\repeatercrossbow}{Repeater Crossbow}
\newcommand{\repeaterhandbow}{Repeater Handbow}

% Army Model Rules Texts

\newcommand{\scentofblooddef}{%
	\newrule{While Engaged in Combat, t}he model gains \textbf{Fearless} and \textbf{Frenzy}.%
}
\newcommand{\fleetcommanderdef}{%
	The model \newrule{part} gains \textbf{Kraken's Hide}. \newrule{Model parts with Harnessed or Inanimate are not affected.}\newline%
	For each Character with Fleet Commander in the army, a single unit of Corsairs may be upgraded with Vanguard.%
}
\newcommand{\beastmasterdef}{%
	Discipline Tests of all friendly Hydras and Krakens within \distance{12} of one or more Characters with Beast Master are subject to Minimised Roll.\newline%
	At the start of each Melee Phase, choose one friendly Hydra, Kraken, or Manticore (the rider is not affected) within \distance{12} of the Beast Master. This model part must reroll failed to-hit rolls with its Close Combat Attacks during this phase.%
}

\newcommand{\killerinstinctdef}{%
	\newrule{Natural to-wound rolls of \result{1} from Close Combat Attacks with Killer Instinct \textbf{must} be rerolled.}%
}
\newcommand{\deathtrancedef}{%
	\newrule{Close Combat Attacks with Death Trance gain} +1 to wound during the First Round of Combat. Close Combat Attacks that \newrule{gain} Death Trance from more than one source gain +1 to wound during all Rounds of Combat instead.%
}

\newcommand{\krakenshidedef}{%
	If \newrule{the wearer's model is} mounted, the wearer gains +1 Armour. If on foot, the wearer gains +2 Armour.%
}
