
\newcommand{\cults}{Cults}
\newcommand{\cultsInitial}{Cu}

\newcommand{\cultgeneral}{Cult General}
\newcommand{\cultrivalry}{Cult Rivalry}
\newcommand{\cultofnabh}{Cult of Nabh}
\newcommand{\cultofyema}{Cult of Yema}
\newcommand{\cultofcadaron}{Cult of Cadaron}
\newcommand{\cultofolaron}{Cult of Olaron}

\newcommand{\cultsintro}{%
	Each Cult rule may be a combination of several different types of Model Rules and Army Specific Rules. Each part is defined in the Cult's rules and follows the rules for its type of Model Rule. Cults are given to model parts. Any Attack Attributes are applied to that model part only, while Universal Rules and Personal Protections are applied to the Multipart Model.
}

\newcommand{\cultgeneraldef}{%
	If the General belongs to a Cult and the Army List does not include any models from any other Cult, then all Corsairs, Dread Legionnaires, and Repeater Auxiliaries gain the same Cult rules as the General.%
}
\newcommand{\cultrivalrydef}{%
	A model can never belong to more than one Cult. Characters belonging to a Cult cannot join units \newrule{that} contain any model from another Cult.%
}

\newcommand{\cultofnabhURdef}{%
	The model gains \textbf{Cult Rivalry}.%
}
\newcommand{\cultofnabhAAdef}{%
	The model part gains \textbf{Hatred} and loses Killer Instinct if it had it.%
}
	
\newcommand{\cultofyemaURdef}{%
	The model gains \textbf{Cult Rivalry}, \textbf{Strider}, +\distance{1} Advance Rate, and +\distance{2} March Rate\removedrule{ (this also affects mounts)}.%
}
\newcommand{\cultofyemaAAdef}{%
	The model part loses Killer Instinct if it had it.%
}
	

\newcommand{\cultofcadaronURdef}{%
	The model gains \textbf{Cult Rivalry}.%
}
\newcommand{\cultofcadaronAAdef}{%
	Shooting Attacks made by the model part gain +1 to hit when shooting at Short Range. A model part with Cult of Cadaron and a Shooting Weapon loses Killer Instinct if it had it.%
}
	
\newcommand{\cultofolarondef}{%
	The model gains \textbf{Cult Rivalry}. Discipline Tests taken by Dread Princes with Cult of Olaron and their units are subject to Minimised Roll. All other models with Cult of Olaron gain +1 Discipline instead.%
}
