
\newgamingscenario{3}{6}{Multiple Objectives}
\label{MultipleObjectives}

\subsection*{Deployment}

Any of the \rewordedrule{standard} \rewordedrule{D}eployment \rewordedrule{T}ypes.

\subsection*{Pre-Game Set-up}

\rewordedrule{After step 8 of the Pre-Game Sequence (immediately} before \rewordedrule{the} Deployment\rewordedrule{Phase)}, \rewordedrule{each} player generate\rewordedrule{s} 3 Tasks \rewordedrule{for themselves} from the list below\rewordedrule{, starting with the player that chose their Deployment Zone}. To generate a Task, roll a D3 and a D6.

\subsection*{Winning the Secondary Objective}

At the end of the game, the player who has completed the most of their assigned Tasks wins th\rewordedrule{is} Secondary Objective.

\startmultipletaskstable{D3 Result}{D6 Result}{Task}
\newtaskfortable{1}{1}{Many Spies \rewordedrule{h}ave Many Eyes}{%
	\rewordedrule{All enemy} units with Scout \rewordedrule{must be removed as casualties} at the end of the game. If the\rewordedrule{re are} no units with Scout \rewordedrule{in the opponent's Army List}, \rewordedrule{all enemy} units with Vanguard \rewordedrule{must be removed as casualties} at the end of the game \rewordedrule{instead}. Generate another Task if \rewordedrule{there are} no units with Scout or Vanguard \rewordedrule{in the opponent's Army List}.%
}
\newtaskfortable{1}{2}{Knowledge is Power}{%
	\rewordedrule{Immediately c}hoose a Wizard in your army. \rewordedrule{T}hat Wizard \rewordedrule{must still be alive} at the end of the game. Generate another Task \rewordedrule{i}f \rewordedrule{there is no Wizard in} your army.%
}
\newtaskfortable{1}{3}{There can be \rewordedrule{O}nly \rewordedrule{O}ne}{%
	\rewordedrule{You must have exactly} one Character \rewordedrule{still alive} at the end of the game. Generate another Task if you only have a single Character in your \rewordedrule{Army List}. \rewordedrule{Unless selected as a mount for a Character, War Platforms are ignored for this Task.}%
}
\newtaskfortable{1}{4}{Steal their \rewordedrule{L}and}{%
	\rewordedrule{Y}ou \rewordedrule{must} have a\rewordedrule{t least one} Scoring Unit \rewordedrule{inside} the enemy Deployment Zone at the start of any of your \rewordedrule{first four P}layer \rewordedrule{T}urns. Units that \rewordedrule{used Special Deployment} are ignored for this purpose.%
}
\newtaskfortable{1}{5}{Seize that Resource}{%
	\rewordedrule{Immediately choose} a \rewordedrule{Terrain Feature} \rewordedrule{completely} outside your \rewordedrule{D}eployment \rewordedrule{Z}one. \rewordedrule{Y}ou \rewordedrule{must} have more Scoring Units within \distance{6} of that \rewordedrule{Terrain Feature} than your opponent at the end of Game Turn 5.%
}
\newtaskfortable{1}{6}{Spring the Trap}{%
	\rewordedrule{At least one of your units} \rewordedrule{must} successfully \rewordedrule{C}harge an enemy unit in the Rear \rewordedrule{Facing}.%
}
\closemultipletaskstable

\newpage
\startmultipletaskstable{D3 Result}{D6 Result}{Task}
\newtaskfortable{2}{1}{Precious Cargo}{%
	\rewordedrule{Immediately c}hoose a Scoring \rewordedrule{U}nit \rewordedrule{in} your army. \rewordedrule{T}hat Scoring Unit \rewordedrule{must still be alive} at the end of the game.%
}
\newtaskfortable{2}{2}{Honour is Everything}{%
	\rewordedrule{None of your units must ever d}eclare a Flee \rewordedrule{C}harge \rewordedrule{R}eaction (\rewordedrule{not even involuntarily}). Generate another Task if \rewordedrule{there are} no units \rewordedrule{in your Army List} that can declare a Flee \rewordedrule{C}harge \rewordedrule{R}eaction.%
}
\newtaskfortable{2}{3}{Onwards Men}{%
	\rewordedrule{Y}our Battle Standard Bearer \rewordedrule{must} successfully \rewordedrule{C}harge an enemy unit and survive until the end of the following \rewordedrule{P}layer \rewordedrule{T}urn \rewordedrule{at least once}. Generate another Task if \rewordedrule{there is} no Battle Standard Bearer \rewordedrule{in your Army List}.%
}
\newtaskfortable{2}{4}{Bring It Down!}{%
	\rewordedrule{Immediately c}hoose a model with Towering Presence in the opponent's army. \rewordedrule{That model must have been removed as a casualty} before the end of Game Turn 4. Generate another Task if the\rewordedrule{re are no models with} Towering Presence \rewordedrule{in the opponent's Army List}.%
}
\newtaskfortable{2}{5}{Thinning Out the Herd}{%
	\rewordedrule{When you generate this Task, i}dentify the unit with the most models \rewordedrule{in} your \rewordedrule{A}rmy \rewordedrule{List}. I\rewordedrule{n case of} a tie, choose one of them. \rewordedrule{T}hat unit \rewordedrule{must have been removed as a casualty} \rewordedrule{by} the end of the game.%
}
\newtaskfortable{2}{6}{Assassination}{%
	\rewordedrule{T}he enemy \rewordedrule{G}eneral \rewordedrule{must be removed as a casualty} before your own \rewordedrule{G}eneral is \rewordedrule{removed as a casualty}.%
}
\hline
\newtaskfortable{3}{1}{Domination}{%
	\rewordedrule{Y}ou \rewordedrule{must} have more Scoring \rewordedrule{U}nits within \distance{6} of the centre of the \rewordedrule{board} than your opponent \rewordedrule{at the end of the game}.%
}
\newtaskfortable{3}{2}{Clear the Skies}{%
	\rewordedrule{All enemy models with Fly must be removed as casualties} at the end of the game. Generate another Task if \rewordedrule{there are no models with Fly in the opponent's Army List}.%
}
\newtaskfortable{3}{3}{Magical Relic}{%
	\rewordedrule{Immediately p}lace a Relic Marker \rewordedrule{with its centre inside} your \rewordedrule{D}eployment \rewordedrule{Z}one. Each time a \rewordedrule{friendly model successfully casts a} non-\rewordedrule{B}ound \rewordedrule{non-Attribute} Spell, you may move the Relic Marker up to \distance{3} in any direction. \rewordedrule{There must never be} any enemy units within \distance{6} of the Relic Marker\rewordedrule{'s centre at the beginning of any of your Players Turns.}%
}
\newtaskfortable{3}{4}{Mutiny}{%
	\rewordedrule{Your General must have been removed as a casualty and \rewordedrule{at least} one of your other Characters must still be on the board by the end of the game.} Generate another Task if \rewordedrule{there is only} a single Character in your \rewordedrule{A}rmy \rewordedrule{List}.%
}
\newtaskfortable{3}{5}{Message}{%
	\rewordedrule{Immediately c}hoose a \rewordedrule{C}haracter in your army. \rewordedrule{T}hat \rewordedrule{C}haracter \rewordedrule{must be} inside the opponent's Deployment Zone at the start of a\rewordedrule{t least one} of your \rewordedrule{P}layer \rewordedrule{T}urns \rewordedrule{during} Game Turn 4 \rewordedrule{or later}.%
}
\newtaskfortable{3}{6}{Target Strike}{%
	\rewordedrule{Immediately c}hoose an enemy Scoring Unit. \rewordedrule{T}hat unit \rewordedrule{must have been removed as a casualty by} the end of the game.%
}
\closemultipletaskstable
