
\newnarrativescenario{5}{An Eye \rewordedrule{o}n the Future}
\label{AnEyeintheFuture}

\flufffont{Few are the ones able to for\rewordedrule{e}see the future, and fewer still the ones able to do so and keep their sanity. The Oracle's prediction can help you reach glory\ldots{} or madness.}

\subsection*{Deployment}

Any of the standard \rewordedrule{D}eployment \rewordedrule{T}ypes.

\subsection*{Pre-Game Set-up}

You need a model to represent the Oracle. It can typically be a \rewordedrule{W}izard, a monster\rewordedrule{,} or even a tower which the Oracle is supposed to be \rewordedrule{in}. \rewordedrule{During} the game, \rewordedrule{that model} is treated as \rewordedrule{I}mpassable \rewordedrule{T}errain. Place \rewordedrule{at} in the cent\rewordedrule{re} of the \rewordedrule{board}.

\subsection*{Scenario Special Rules}

\subsubsection*{The Great Oracle}

At the end of your \rewordedrule{M}ovement \rewordedrule{P}hase, you may ask \rewordedrule{the Oracle} for predictions for each friendly Character \rewordedrule{that is not Fleeing 	and not} \rewordedrule{E}ngaged in \rewordedrule{C}ombat within \distance{3} of the \rewordedrule{O}racle. For each \rewordedrule{C}haracter, roll a D6 and place \rewordedrule{it} next to the \rewordedrule{C}haracter\rewordedrule{, referred to as} a Fate Di\rewordedrule{c}e. \rewordedrule{When performing one of the following actions}, you may replace any single rolled D6 with the Fate Di\rewordedrule{c}e \rewordedrule{(this is not considered rerolling the dice)}.

\begin{itemize}
\item Casting Attempts made by the Character
\item To-hit rolls \rewordedrule{for attacks} made by the Character
\item To-wound rolls \rewordedrule{for attacks} made by the Character
\item Armour Save rolls \rewordedrule{made} the Character
\item Special Save rolls \rewordedrule{made} by the Character
\item Charge Range rolls \rewordedrule{for} the Character or its unit
\end{itemize}

\rewordedrule{A}s long as a Character has a Fate Di\rewordedrule{c}e, it suffers a \rewordedrule{negative} modifier to its Discipline equal to half the value o\rewordedrule{f} the Fate Di\rewordedrule{c}e, \rewordedrule{rounding fractions} up. No Character can have more than a single Fate Di\rewordedrule{c}e.

\subsection*{Winning the Scenario}

The players fight to gain the loyalty of the Oracle. \rewordedrule{Each} time \rewordedrule{a Character or a unit is removed as a casualty within \distance{18} of the Oracle, and each time a unit Breaks within \distance{18} of the Oracle, the opponent of its owner gains 1 Victory Counter. Each unit can only award a single Victory Token per phase.}

At the end of the game, the player with the most Victory Counters wins the game.
