\part*{Gaming Scenarios}
\label{gaming_scenarios}

These scenarios are intended to be used for everyday gaming, and can be played using any armies and normal \rewordedrule{T}errain\rewordedrule{, replacing} the normal Deployment Types and Secondary Objectives \rewordedrule{in the Rulebook}.

Each Gaming Scenario \rewordedrule{consists of the following elements:}

\startgamingscenarioheadings%
\gamingscenarioheading{Deployment} \rewordedrule{T}he Deployment Type used in the scenario. This can be one of the standard Deployment Types but it can also be \rewordedrule{unique}. If so, everything needed to carry out the \rewordedrule{D}eployment will be specified.

\gamingscenarioheading{Pre-Game Set-up} \rewordedrule{Which steps to perform} place before the battle begins, such as placing tokens for the Secondary Objective. 

\gamingscenarioheading{Scenario Special Rules} \rewordedrule{A}ny unique rules that affect the armies or the \rewordedrule{B}attlefield in this \rewordedrule{s}cenario.

\gamingscenarioheading{Winning the Secondary Objective} \rewordedrule{H}ow \rewordedrule{to win} the Secondary Objective. If there is a winner of the Secondary Objective, that player gains 3 additional Battle Points while the loser of the Secondary Objective loses 3 Battle Points, as usual.
\closegamingscenarioheadings%

\subsection*{Scenario Chart}

You can use the following \rewordedrule{chart} to \rewordedrule{randomly} determine which scenario to play. \rewordedrule{R}oll a D3 to choose the scenario bracket (see \rewordedrule{the} table \rewordedrule{below})\rewordedrule{, and} then roll a D6 to determine the exact scenario to be played.

\startgamingscenariolist
\textbf{D3 Result}&
\textbf{D6 Result}&
\textbf{Scenario}&
\textbf{Page}\\
1&
1&
\hyperref[Misdirections]{Misdirections}&
\pageref{Misdirections}\\
1&
2&
\hyperref[HiddenTreasures]{Hidden Treasures}&
\pageref{HiddenTreasures}\\
1&
3&
\hyperref[DarkVisions]{\rewordedrule{Dark Visions}}&
\pageref{DarkVisions}\\
1&
4&
\hyperref[LostRuins]{Lost Ruins}&
\pageref{LostRuins}\\
1&
5&
\hyperref[AncientArtefact]{Ancient Artefact}&
\pageref{AncientArtefact}\\
1&
6&
\hyperref[TheAdversarysTask]{The Adversary's Task}&
\pageref{TheAdversarysTask}\\
\hline
2&
1&
\hyperref[TheLongMarchHome]{The Long March Home}&
\pageref{TheLongMarchHome}\\
2&
2&
\hyperref[MeteorShower]{Meteor Shower}&
\pageref{MeteorShower}\\
2&
3&
\hyperref[TheHolyGrail]{The Holy Grail}&
\pageref{TheHolyGrail}\\
2&
4&
\hyperref[TheHiddenKings]{The Hidden Kings}&
\pageref{TheHiddenKings}\\
2&
5&
\hyperref[TheHiddenKings]{Despoilers}&
\pageref{TheHiddenKings}\\
2&
6&
\hyperref[DominatingTheField]{Dominating the Field}&
\pageref{DominatingTheField}\\
\hline
3&
1&
\hyperref[BarrelOfStout]{Barrel of Stout}&
\pageref{BarrelOfStout}\\
3&
2&
\hyperref[EscapeFromBeyondTheVeil]{Escape from Beyond the Veil}&
\pageref{EscapeFromBeyondTheVeil}\\
3&
3&
\hyperref[Carnage]{Carnage}&
\pageref{Carnage}\\
3&
4&
\hyperref[HoldTheLine]{Hold the Line}&
\pageref{HoldTheLine}\\
3&
5&
\hyperref[FoulManners]{Foul Manners}&
\pageref{FoulManners}\\
3&
6&
\hyperref[MultipleObjectives]{Multiple Objectives}&
\pageref{MultipleObjectives}\\
\closegamingscenariolist
