

%%%% Unit entries names

% CHARACTERS

\newcommand{\vermindaemon}{Vermin Daemon}
\newcommand{\tyrant}{Tyrant}
\newcommand{\chief}{Chief}
\newcommand{\magister}{Magister}
\newcommand{\rakachitmachinist}{Rakachit Machinist}
\newcommand{\sicarraassassin}{Sicarra Assassin}
\newcommand{\plaguepatriarch}{Plague Patriarch}

% MOUNTS

\newcommand{\verminguardlitter}{Vermin Guard Litter}

\newcommand{\verminhulkbodyguard}{Vermin Hulk Bodyguard}
\newcommand{\verminhulkbodyguardQRS}{VH Bodyguard}
\newcommand{\verminhulkbodyguardSHORT}{VH Bodyguard}

\newcommand{\monstrousrat}{Monstrous Rat}

\newcommand{\plaguependulum}{Plague Pendulum}
 \newcommand{\chassis}{Chassis}
 \newcommand{\ram}{Ram}
 
\newcommand{\doombell}{Doom Bell}

% CORE

\newcommand{\ratsatarms}{Rats-at-Arms}
\newcommand{\ratatarms}{Rat-at-Arms}

\newcommand{\verminguard}{Vermin Guard}
\newcommand{\verminguardSINGULAR}{Vermin Guard}

\newcommand{\plaguebrotherhood}{Plague Brotherhood}
\newcommand{\plaguebrother}{Plague Brother}

\newcommand{\slaves}{Slaves}
\newcommand{\slave}{Slave}

\newcommand{\footpads}{Footpads}
\newcommand{\footpad}{Footpad}

% SPECIAL

\newcommand{\giantrats}{Giant Rats}
\newcommand{\giantrat}{Giant Rat}

\newcommand{\plaguedisciples}{Plague Disciples}
\newcommand{\plaguedisciple}{Plague Disciple}

\newcommand{\verminhulks}{Vermin Hulks}
\newcommand{\verminhulk}{Vermin Hulk}

\newcommand{\ratswarms}{Rat Swarms}
\newcommand{\ratswarm}{Rat Swarm}

% Meat Grinder already defined as a Model Rule

\newcommand{\gutterblades}{Gutter Blades}
\newcommand{\gutterblade}{Gutter Blade}

% TUNNEL GUNNERS

\newcommand{\weaponteam}{Weapon Team}

\newcommand{\jezails}{Jezails}% Singular already defined as a Model Rule

\newcommand{\grenadiers}{Grenadiers}
\newcommand{\grenadier}{Grenadier}

\newcommand{\plaguecatapult}{Plague Catapult}
\newcommand{\crew}{Crew}

\newcommand{\lightningcannon}{Lightning Cannon}

\newcommand{\dreadmill}{Dreadmill}

% BUILT AND BRED

\newcommand{\abomination}{Abomination}


%%%% Unit entries rules

%% CHARACTERS

% Vermin Daemon

\newcommand{\againstmagicalattacks}{against Magical Attacks}
\newcommand{\schemer}{Schemer}
\newcommand{\schemerdef}{%
	The model knows one additional spell. \newrule{In addition, spells cast by the model gain +\distance{3} range.} If a Vermin Daemon is part of the army, the Tunnel Gunners Category is reduced to \enquote{Max. \SI{25}{\percent}}.%
}

% Chief

\newcommand{\fetthisbroodmaster}{Fetthis Broodmaster}
\newcommand{\fetthisbroodmasterdef}{%
	The \newrule{model}'s Advance Rate is \textbf{set} to \distance{7}, its March Rate is \textbf{set} to \distance{14}, and it gains \textbf{\swiftstride}.%
}

% Rakachit Machinist

\newcommand{\mechanicallimbs}{Mechanical Limbs}
\newcommand{\mechanicallimbsdef}{%
	\newrule{The model} may use one of the attacks \newrule{below} once per Player Turn. If used as a Shooting Attack, the attack may be used in addition to using a Shooting Weapon, provided both Shooting Attacks target the same unit.%
	\begin{smallitemize}%
		\item \textbf{Lightning Coil:} Shooting Attack. \range{18}, \shots{\Dsix}, \St{} 2, \AP{} 3. This attack hits automatically.%
		\item \textbf{Naphta Thrower:} \textbf{\breathattack{} (\St{} 3, \AP{} 0, \flamingattacks{})}. This Breath Attack is not limited to being used only once per game.%
	\end{smallitemize}%
}

% Sicarra Assassin

\newcommand{\againstcharacter}{against Character}
\newcommand{\sicarraassassinnote}{%
	Affects only attacks made with Close Combat and Shooting Weapons that are not enchanted.%
}
\newcommand{\professionalcourtesy}{Professional Courtesy}
\newcommand{\professionalcourtesydef}{%
	\newrule{The model} cannot join or be deployed in units that contain another \newrule{model with Professional Courtesy}. \newrule{The model} may perform Make Way moves even when it is in base contact with an enemy model.%
}

% Plague Patriarch

\newcommand{\instancesofdarkshard}{\newrule{instances of} Dark Shard}
\newcommand{\putridscholar}{Putrid Scholar}
\newcommand{\putridscholardef}{%
	The model selects its spells from all Learned Spells of \newrule{Occultism} and \spellformat{\theawakenedswarm}{\hereditaryspell}. This overrides the normal Spell Selection rules connected to being a Wizard Apprentice or Adept.%
}

%% MOUNTS

% Vermin Guard Litter

\newcommand{\herdingtheswarm}{Herding the Swarm}
\newcommand{\herdingtheswarmdef}{%
	The model's range of Commanding Presence (if available) is increased by \distance{6}.%
}

% Plague Pendulum

\newcommand{\pendulum}{Pendulum}
\newcommand{\pendulumdef}{%
	The model part can only use its Grind Attacks against enemy units Engaged in the model's Front Facing.%
}

% Doom Bell

\newcommand{\abovethemasses}{Above the Masses}
\newcommand{\abovethemassesdef}{%
	When \newrule{the rider} chooses targets for spells with type Direct, it ignores the restriction of only choosing targets in its Front Arc. When \newrule{the rider} chooses targets for spells with type Missile, it can draw Line of Sight at \SI{360}{\degree} from any point of the \newrule{model}'s base, and may cast Missile spells even when Engaged in Combat. All non-Bound Spells cast by the \newrule{rider} gain +\distance{3} range.%
}
\newcommand{\soundingthebell}{Sounding the Bell}
\newcommand{\soundingthebelldef}{%
	Enemy units within \distance{18} of one or more models with this Universal Rule suffer \minuss{}1 Offensive Skill and \minuss{}1 Defensive Skill. At the start of each friendly Magic Phase, the owner may choose to roll a D6. On 2+, the Offensive and Defensive Skill modifiers are increased to \minuss{}2 each, until the start of the next friendly Magic Phase. If a \result{1} is rolled, the \newrule{model} loses Sounding the Bell until the \newrule{start of the next friendly Magic Phase}, and all units (friend and foe) with models in base contact with the \newrule{model} suffer D6 hits with Strength 4 and Armour Penetration 2.%
}

%% CORE

% Slaves

\newcommand{\disposable}{Disposable}
\newcommand{\disposabledef}{%
	If the unit Breaks from Combat, it is immediately removed as a casualty. When checking if an enemy unit is Steadfast,
\newrule{friendly} Slave units count as having 0 Full Ranks, unless the Slave unit is Engaged in the enemy unit's Flank or Rear Facing. When shooting into a combat where the only Engaged friendly models are Slaves:%
	\begin{smallitemize}%
		\item The Shooting Attack gains +2 to hit.%
		\item When randomising to see which unit is hit, the intended target is hit on 4+ (instead of 3+).%
	\end{smallitemize}%
}


%% SPECIAL

% Vermin Hulks

\newcommand{\thunderhulk}{Thunder Hulk}
\newcommand{\thunderhulkdef}{%
	The model gains Heavy Armour and its base size is changed to 50\timess{}\SI{50}{\milli\meter}.%
}
\newcommand{\ifthunderhulk}{If \textbf{\thunderhulk{}}}

% Rat Swarms

\newcommand{\tinyrule}{Tiny}
\newcommand{\tinyruledef}{%
	The model ignores friendly units when moving in the Charge and Movement Phase, but must follow the Unit Spacing rule at the end of the move.%
}

% Meat Grinder

\newcommand{\onewiththeswarm}{One with the Swarm}
\newcommand{\onewiththeswarmdef}{%
	The model can only join units of Rats-at-Arms\removedrule{ and loses Insignificant while joined to such units}.%
}


%% TUNNEL GUNNERS

% Weapon Team

\newcommand{\scorchedfur}{Scorched Fur}
\newcommand{\scorchedfurdef}{%
	When the model rolls Breakdown on the Misfire Table, it is removed as a casualty.%
}

% Jezails

\newcommand{\pavise}{Pavise}
\newcommand{\pavisedef}{%
	The model gains +3 Armour against Ranged Attacks.%
}

% Catapult and Cannon

\newcommand{\verminousartilleryrestriction}{%
	\plaguecatapult{} and \lightningcannon{} share the same \zerotoXunitsperarmy{2} limitation.%
}
\newcommand{\lightningcannondef}{%
	Before rolling to hit, the Lightning Cannon may be supercharged. If supercharged, the weapon's Strength is \textbf{set} to 10 and its range is \textbf{set} to \distance{18} for the duration of the phase. After the shot has been resolved, roll a D6. On a roll of \result{1} or \result{2}, the Lightning Cannon cannot be supercharged again until the end of game.%
}

% Dreadmill

\newcommand{\electricdischarge}{Electric Discharge}
\newcommand{\electricdischargedef}{%
	\newrule{Models can use} this Special Attack as \newrule{a)} a Shooting Attack, and as \newrule{b)} a Special Attack when Engaged in Combat.%
	\begin{enumerate}[label=\alph*)]%
		\item Choose a target using the normal rules for Shooting Attacks. The Shooting Attack has \range{18}, \shots{3}, \textbf{\accurate{}}, \textbf{\quicktofire{}}, \textbf{\reload{}}, and Aim (4+).%
		\item The Melee Attack is made at the model part's Initiative Step. Choose a single enemy unit in base contact and roll three D6 (these rolls are not considered to-hit rolls). For each roll of 3+, the target suffers a hit from the Electric Discharge.%
	\end{enumerate}%
	Hits from the Electric Discharge are resolved with Strength 5, Armour Penetration 10, \textbf{Lightning Attack}, \textbf{Magical Attacks}, and \textbf{Multiple Wounds (D3)}. Before using the Electric Discharge, the Dreadmill may be supercharged. If supercharged, the Strength of attacks from the Electric Discharge is \textbf{set} to 6 and their range is \textbf{set} to \distance{12} for the duration of the phase. After the Electric Discharge has been resolved, roll a D6. On a roll of \result{1} or \result{2}, the Dreadmill cannot be supercharged again until the end of the game.%
}

