
\maintitle{BHchangelog}{\changelog}

\subtitle{0.205.2}

\begin{itemize}
\item Logotype on the titlepage changed for our new logotype.
\item Area Attack, updated with the reverted order of X and Y.
\item Bug with the spacing around headers corrected.
\end{itemize}

\subtitle{0.205.1}

\begin{itemize}
\item Blue and green from 0.205.0 removed.
\item Briar Beast, Sleeper rule reworded.
\item Beast Giant, Big Borther rule reworded.
\end{itemize}


\subtitle{0.205.0}

\begin{itemize}
\item Blue and green from 0.204 removed.
\item Standardisation of the formatting of lists.
\item Confusion between hyphen (-), en-dash (--), em-dash (---) and minus symbol (−) corrected.
\item \enquote{x} replaced with \enquote{\timess{}} as the mathematical times symbol (for example in 25\timess{}50).
\item Replace Hard Target with Hard Target (1), Last one Turn with One Turn, Catapult(X) with Catapult (X\timess{}X).
\item Beta for the Quick Reference Sheet, check it and give us feedback!
\end{itemize}

Un-nesting rulebook model rules. Models given rules that used to be nested in other rules.
\begin{itemize}
\item Light Troops and Swiftstride no longer part of Fly.
\item Fearless no longer part of Frenzy.
\item Hard Target and Light Troops no longer part of Skirmisher.
\item Fear no longer part of Terror.
\item Fearless no longer part of Unbreakable, Unstable, or Supernal.
\item Move or Fire no longer part of War Machine.
\item Not a Leader no longer part of War Platforms.
\end{itemize}

%\subtitle{Model Rules}
%
%\begin{itemize}[label={-}]
%
%\end{itemize}

%\subtitle{Totems}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Hereditary}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Special Equipment}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Characters}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Core}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Special}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

\subtitle{Terrors of the Wild}

\begin{itemize}
\item Beast Giant, new Big Brother upgrade for all Giant.
\end{itemize}

\subtitle{Points}
\begin{itemize}
\item Hawthorn's Curse 70
\item Wild Form 35
\item Twin hungers 40
\item Inscribing Burin 30
\item Minotaur Chieftain 220
\item Wildhorns shield as default (150+10), may exchange shield for:
- paired 2
- throwing 2
- paired+throwing 4
\item Mongrel Raiders Start 95
- Additional 7
\item Jabberwock 340
\end{itemize}


