
%%%% Unit entries names

% CHARACTERS

\newcommand{\beastlord}{Beast Lord}
\newcommand{\beastchieftain}{Beast Chieftain}
\newcommand{\soothsayer}{Soothsayer}
\newcommand{\minotaurwarlord}{Minotaur Warlord}
\newcommand{\minotaurchieftain}{Minotaur Chieftain}
\newcommand{\centaurchieftain}{Centaur Chieftain}

% MOUNTS

\newcommand{\raidingchariot}{Raiding Chariot}
\newcommand{\wildhorncrew}{Wildhorn Crew}
\newcommand{\warhog}{War Hog}
\newcommand{\chassis}{Chassis}
 
\newcommand{\razortuskchariot}{Razortusk Chariot}
\newcommand{\razortusk}{Razortusk}

% CORE

\newcommand{\wildhornherd}{Wildhorn Herd}
\newcommand{\wildhorn}{Wildhorn}

\newcommand{\mongrelherd}{Mongrel Herd}
\newcommand{\mongrel}{Mongrel}

\newcommand{\mongrelraiders}{Mongrel Raiders}
\newcommand{\mongrelraider}{Mongrel Raider}

% SPECIAL

\newcommand{\feralhound}{Feral Hound}
\newcommand{\feralhounds}{Feral Hounds}

\newcommand{\longhornherd}{Longhorn Herd}
\newcommand{\longhorn}{Longhorn}

\newcommand{\minotaur}{Minotaur}
\newcommand{\minotaurs}{Minotaurs}

\newcommand{\centaur}{Centaur}
\newcommand{\centaurs}{Centaurs}

% Raiding Chariot - already defined in mounts
\newcommand{\longhorncrew}{Longhorn Crew}

\newcommand{\razortuskherd}{Razortusk Herd}

% Razortusk Chariot - already defined in mounts

\newcommand{\briarbeast}{Briar Beast}
\newcommand{\briarbeasts}{Briar Beasts}

\newcommand{\gargoyle}{Gargoyle}
\newcommand{\gargoyles}{Gargoyles}

% TERRORS OF THE WILD

\newcommand{\cyclops}{Cyclops}

\newcommand{\gortach}{Gortach}

\newcommand{\jabberwock}{Jabberwock}

\newcommand{\beastgiant}{Beast Giant}


%%%% Unit entries rules

%% CHARACTERS

% Beast Lord

\newcommand{\ifgeneral}{If General}

% Soothsayer

\newcommand{\bloodoffering}{Blood Offering}
\newcommand{\bloodofferingdef}{%
A unit that includes at least one Character with \bloodoffering{} may reroll failed Panic Tests at the cost of inflicting one wound with no saves of any kind allowed to a Character with \bloodoffering{} in the unit.
}


%% MOUNTS

% Razortusk Chariot

\newcommand{\huntinghorn}{Hunting Horn}
\newcommand{\huntinghorndef}{%
All friendly units within \distance{6} of one or more models with Hunting Horn gain \distance{+1} to their Charge Range rolls.
}


%% CORE

% Wildhorn Herd

\newcommand{\ambushcategorynote}{This unit counts towards \ambushpredators{} if Ambushing.}


%% SPECIAL

% Longhorn Herd

\newcommand{\replacehalberdwithgw}{Replace \halberd{} with \gw{}}

% Briar Beast

\newcommand{\sleeper}{Sleeper}
\newcommand{\sleeperdef}{%
The model follows the rules for \ambush{} with the following exceptions:
\begin{smallitemize}%
\item At the end of step 2 of the owner's Movement Phase Sequence (including the owner's Player Turn 1), the owner may decide for each of their \briarbeasts{} if they will enter the Battlefield or not (no dice rolls are required).
\item When the model enters the Battlefield, it must be placed completely within any Forest Terrain Feature instead of having its Rear Facing touch the Board Edge. If the model cannot be placed, it cannot enter the Battlefield this turn.
\end{smallitemize}%
}


%% TERRORS OF THE WILD

% Cyclops

\newcommand{\hurlattack}{Hurl Attack}
\newcommand{\hurlattackdef}{%
\textbf{\catapult{} (4)}. \range{6-36}, \shots{1}, \St{} 3 [7], \AP{} 0 [4], \textbf{\divineattacks}, \textbf{\magicalattacks}, [\textbf{\multiplewounds{D3, \clippedwings{}}{}}]. A \cyclops{} that only Pivots (and moves no further) during its owner's Movement Phase ignores the to-hit modifier from Moving and Shooting in the next Shooting Phase.
}

% Gortarch

\newcommand{\strengthfromflesh}{Strength from Flesh}
\newcommand{\strengthfromfleshdef}{%
Whenever a \gortach{} inflicts an unsaved \lethalstrike{} (rolling a natural \result{6} to wound with a Close Combat Attack with \lethalstrike{}), the attack gains \textbf{\multiplewounds{D3}{}}, and the \gortach{} Recovers 1 Health Point at the end of the Initiative Step (unless the Gortach was removed as a casualty in this Initiative Step). No more than 1 Health Point may be Recovered by each \gortach{} per phase in this manner.
}

% Jabberwock

\newcommand{\auraofmadness}{Aura of Madness}
\newcommand{\auraofmadnessdef}{%
Enemy units within \distance{6} of one or more models with \auraofmadness{} suffer -1 Discipline.
}

% Beast Giant

\newcommand{\giantseegiantdo}{Giant See, Giant Do}
\newcommand{\rage}{Rage}
\newcommand{\giantclub}{Giant Club}
\newcommand{\uprootedtree}{Uprooted Tree}
\newcommand{\beerbarrel}{Beer Barrel}

\newcommand{\giantseegiantdodef}{%
The model gains \textbf{\drunkard} and \textbf{\strider{\forest}}. At the end of a friendly Movement Phase, if the model is in contact with a Forest Terrain Feature it may lose its current weapon (if applicable) and gain \uprootedtree{}.
}
\newcommand{\ragedef}{%
Whenever the model loses a Health Point, it gains +1 Attack Value. Whenever it gains a Health Point, it suffers -1 Attack Value.
}
\newcommand{\giantclubdef}{%
Attacks made with this weapon gain +1 Strength and +1 Armour Penetration.
}
\newcommand{\uprootedtreedef}{%
Attacks made with this weapon hit automatically and have their Strength \textbf{set} to 5 and their Armour Penetration \textbf{set} to 0.
}
\newcommand{\beerbarreldef}{%
The bearer gains \textbf{\lootedbooze}. Once per game, the weapon may be used as a Shooting Weapon with the following profile: \newline
\range{8}, \shots{1}, \St{} 4, \AP{} 0, \textbf{\areaattack{3}}, \textbf{\reload}, hits automatically. After being used as a Shooting Weapon, the bearer loses \lootedbooze{}.
}
