
\maintitle{WDGchangelog}{\changelog}

\subtitle{2.2}

\subtitle{Redesign and rule changes}

\begin{itemize}
\item Favour of Envy, all models of a unit must have the Favour to be able to reroll \result{1} in Charge Range rolls.
\item Favour of Sloth, the effect is now lost for an Advance Move $>$\distance{10} too, and the distance is decreased to \distance{6} for a Gigantic model. No more tax for the Sloth Dragon.
\item Thrice-Forged, Can now also be taken by Large Height. Maximum Armour 5 for models with Towering Presence. This way this armor becomes useful for Chimera riders.
\item Warband Banner changed into Trophy Rack. Does not give Standard Bearer anymore, but allows to take Banner Enchantment, and gives a permanent +1 Combat Score modifier for each Duel won. Standard Bearer on Battleshrine replace with this new rule.
\item Ledger of Souls, reworked. Range \distance{9}, works on any non-Insignificant model, don't increase the Veil Token limite any more.
\item Orb of Foreboding, removed, replaced with Veilgate Orb which increase the Veil Token limit.
\end{itemize}

\subtitle{Balance update}

\begin{itemize}
\item Special Items:
\begin{itemize}
\item Burning Portent 120 \costup{} 130
\item Thrice-Forged 65 \costdown{} 60
\item Icon of the Infinite 50 \costdown{} 40
\item Zealot's Banner 55 \costup{} 60
\item Ledger of Souls 90 \costdown{} 75
\item Orb of Foreboding (now Veilgate Orb) 55 \costdown{} 15
\end{itemize}
\item Chosen Lord:
\begin{itemize} 
\item Trophy Rack 30 \costdown{} 25
\item Envy 20 \costup{} 25
\item Greed 40 \costdown{} 30
\item Wrath 10 \costup{} 20
\item Daemonic Wings 100 \costdown{} 90
\item Karkadan 105 \costdown{} 95
\item Scythed skywheel 130 \costdown{} 120
\item Wasteland Dragon 400 \costdown{} 390
\end{itemize}
\item Doomlord:
\begin{itemize}
\item Trophy Rack 30 \costdown{} 25
\item Spiked Shield 20 \costup{} 25
\item Wasteland Behemoth 245 \costdown{} 225
\end{itemize}
\item Sorcerer:
\begin{itemize}
\item Battleshrine 310 \costdown{} 280
\item Wasteland Behemoth 405 \costdown{} 365
\end{itemize}
\item Barbarian Chief:
\begin{itemize}
\item Trophy Rack 30 \costdown{} 25
\item Wasteland Behemoth 400 \costdown{} 375
\end{itemize}
\item Feldrak Ancestor:
\begin{itemize}
\item Great Weapon 35 \costdown{} 30
\item Halberd 55 \costdown{} 50
\end{itemize}
\item Fallen, additional models 19 \costdown{} 18
\item Barbarians, starting cost 130 \costup{} 135
\item Warrior Knights:
\begin{itemize}
\item Starting cost 245 \costup{} 250
\item Greed 4 \costup{} 5
\item Lust 12 \costdown{} 11
\item Lance 10 \costdown{} 8
\end{itemize}
\item Chosen Chariot, Gluttony 15 \costdown{} 10
\item Forsworn:
\begin{itemize}
\item Starting cost 180 \costup{} 190
\item Spiked Shield 12 \costup{} 13
\end{itemize}
\item Wretched One:
\begin{itemize}
\item Starting cost 105 \costdown{} 95
\item Additional models 90 \costup{} 92
\end{itemize}
\item Battleshrine, starting cost 290 \costdown{} 260
\item Barbarian Horseman, additional models 20 \costdown{} 18
\item Marauding Giant, Monstrous Familiar 55 \costdown{} 50
\item Hellmaw:
\begin{itemize}
\item Starting cost 280 \costdown{} 270
\item One Ominous Gateway 50 \costup{} 75
\item Two Ominous Gateways 150 \costup{} 175
\end{itemize}
\end{itemize}

\subtitle{Clarification and rewording}

\begin{itemize}
\item Fearless and Break Tests rerolls removed from Hell-Forged Armour. Fearless added in the profiles and reroll added to the Paths (Favoured and Exiled) instead. Flavour change.
\item Wasteland Dragon, no more 0--1 restriction as it can only be ridden by the Army General anyway.
\item Hellmaw, Ominous Gateway, Clarification of when it happens. The second part is no longer necessary as now the rules for simultaneous effects apply (and here the player that chose their deployment zone is considered the active player, and the active player's effects are applied first).
\end{itemize}
