% Categories

\newcommand{\legendarybeasts}{Legendary Beasts}
\newcommand{\legendarybeastsinitials}{LB}

% Hereditary Spell

\newcommand{\hellfire}{Hellfire}
\newcommand{\hellfiredef}{%
The target suffers \base{2D3} \boosted{2D6} hits with Strength 6, \newline{}Armour Penetration 0, and Magical Attacks.%
}
\newcommand{\hellfiretarget}{%
The spell can target units Engaged and in base contact with the Caster's Front Facing.%
}

% QRS

\newcommand{\favoursofthedarkgodsreminder}{This is only a short summary. Refer to the corresponding chapters above for the complete rules.}

\newcommand{\envyshortdef}{%
Model part gains Swiftstride and reroll to-hit rolls of \result{1} when Charging. Reroll rolls of \result{1} in Charge Range rolls for units consisting entirely of models with this Favour.%
}
\newcommand{\gluttonyshortdef}{%
Model part gains +1 Strength with Close Combat Attacks for the rest of the game the first time it successfully Charges a Fleeing unit, or wins a combat and doesn't Pursue or Overrun.%
}
\newcommand{\greedshortdef}{%
Bearer gains Great Weapon, Halberd, Paired Weapons, and Weapon Master. +50 pts Special Item allowance.%
}
\newcommand{\lustshortdef}{%
Model gains Strider. Units with majority of models with this Favour gain Feigned Flight, may declare Flee even if Fearless, and then Rally with Minimised Roll the next turn.%
}
\newcommand{\prideshortdef}{%
Minimised Roll for Discipline Tests.%
}
\newcommand{\slothshortdef}{%
Model gains +1 Resilience, unless it declares a \distance{10+} (\distance{6+} for Gigantic) Charge or Advance/March Moves for \distance{10} or more (\distance{6+} for Gigantic) (lost for a Player Turn).%
}
\newcommand{\wrathshortdef}{%
Model part gains Lightning Reflexes and +1 Agility. Enemies gain +1 to hit the model. Effects apply only in the First Round of Combat.%
}
