\maintitle{HBEchangelog}{\changelog}


\subtitle{0.205.2}

\begin{itemize}
\item Logotype on the titlepage changed for our new logotype.
\item Area Attack, updated with the reverted order of X and Y.
\item Bug with the spacing around headers corrected.
\item Favour of Meladys, doesn't need the Focused type.
\end{itemize}

\subtitle{0.205.1}

\begin{itemize}
\item Blue and green from 0.205.0 removed.
\item Phoenix: Magical Attacks removed.
\end{itemize}

\subtitle{0.205.0}

\begin{itemize}
\item Blue and green from 0.204 removed.
\item Standardisation of the formatting of lists.
\item Confusion between hyphen (-), en-dash (--), em-dash (---) and minus symbol (−) corrected.
\item \enquote{x} replaced with \enquote{\timess{}} as the mathematical times symbol (for example in 25\timess{}50).
\item Replace Hard Target with Hard Target (1), Last one Turn with One Turn, Catapult(X) with Catapult (X\timess{}X).
\item Beta for the Quick Reference Sheet, check it and give us feedback!
\end{itemize}

Un-nesting rulebook model rules. Models given rules that used to be nested in other rules.
\begin{itemize}
\item Light Troops and Swiftstride no longer part of Fly.
\item Fearless no longer part of Frenzy.
\item Hard Target and Light Troops no longer part of Skirmisher.
\item Fear no longer part of Terror.
\item Fearless no longer part of Unbreakable, Unstable, or Supernal.
\item Move or Fire no longer part of War Machine.
\item Not a Leader no longer part of War Platforms.
\end{itemize}

%\subtitle{General}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

\subtitle{Army Model Rules}

\begin{itemize}
\item Dragonforged Armour, rewording.
\end{itemize}

%\subtitle{Honours}
%
%\begin{itemize}[label={-}]
%
%\end{itemize}

\subtitle{Special Equipment}

\begin{itemize}
\item Star Metal Alloy, only work while using the shield.
\end{itemize}

%\subtitle{Characters}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

\subtitle{Core}

\begin{itemize}
\item Highborn Lancer, Horses Off 3 (-1).
\end{itemize}

%\subtitle{Special}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Queen's Bows}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

%\subtitle{Naval Ordnance}
%
%\begin{itemize}[label={-}]
%\item 
%\end{itemize}

\subtitle{Ancient Allies}

\begin{itemize}
\item Phoenix, Frosty add supernal, Fire remove magical attacks, Rebirth clarification.
\end{itemize}

\subtitle{Points}
\begin{itemize}
\item High warden of the flame 105
\item Fleet Officer 75
- Giant Eagle 60
- Sky Sloop 300
- Griffon 200
\item Ring of Pearl Throne 90
\item Nova Lance 90
\item Glittering lacquer 40
\item High Prince Griffon Mount 200
\item High Prince Giant Eagle Mount 60
\item Commander Griffon Mount 200
\item Commander Giant Eagle Mount 60
\item Mage Griffon Mount 100
\item Highborn Lancers start 240
- additional 40
\item Sea Guard start 300
- additional 21
\item Grey Watchers start 150
- additional 26
\item Phoenix 375
- Frost free
- Fire 45
\end{itemize}


