
% Unit Entry Names

% Characters

\newcommand{\highprince}{High Prince}
\newcommand{\commander}{Commander}
\newcommand{\mage}{Mage}


% Mounts

\newcommand{\elvenhorse}{Elven Horse}
\newcommand{\gianteagle}{Giant Eagle}
\newcommand{\griffon}{Griffon}
\newcommand{\youngdragon}{Young Dragon}
\newcommand{\dragon}{Dragon}
\newcommand{\ancientdragon}{Ancient Dragon}

\newcommand{\reaverchariot}{Reaver Chariot}
\newcommand{\crew}{Crew}
\newcommand{\chassis}{Chassis}

\newcommand{\lionchariot}{Lion Chariot}
\newcommand{\lion}{Lion}

\newcommand{\skysloop}{Sky Sloop}
\newcommand{\hawk}{Hawk}


% Core

\newcommand{\citizenspears}{Citizen Spears}
\newcommand{\citizenspear}{Citizen Spear}

\newcommand{\highbornlancers}{Highborn Lancers}
\newcommand{\highbornlancer}{Highborn Lancer}

\newcommand{\citizenarchers}{Citizen Archers}
\newcommand{\citizenarcher}{Citizen Archer}

\newcommand{\seaguard}{Sea Guard}
\newcommand{\seaguardSINGULAR}{Sea Guard}

\newcommand{\eleinreavers}{Elein Reavers}
\newcommand{\eleinreaver}{Elein Reaver}


% Special

\newcommand{\swordmasters}{Sword Masters}
\newcommand{\swordmaster}{Sword Master}

\newcommand{\lionguard}{Lion Guard}
\newcommand{\lionguardSINGULAR}{Lion Guard}

\newcommand{\flamewardens}{Flame Wardens}
\newcommand{\flamewarden}{Flame Warden}

\newcommand{\knightsofryma}{Knights of Ryma}
\newcommand{\knightofryma}{Knight of Ryma}

% Reaver and Lion Chariot and Giant Eagle already defined in Mounts
\newcommand{\reaverchariots}{Reaver Chariots}
\newcommand{\gianteagles}{Giant Eagles}


% Queen's Bows

\newcommand{\queensguard}{Queen's Guard}
\newcommand{\queensguardSINGULAR}{Queen's Guard}

\newcommand{\greywatchers}{Grey Watchers}
\newcommand{\greywatcher}{Grey Watcher}


% Naval Ordnance

\newcommand{\seaguardreaper}{Sea Guard Reaper}

% Sky Sloop already defined in Mounts


% Ancient Allies

\newcommand{\phoenix}{Phoenix}



% Unit Entry Rules

%%% CHARACTERS

% High Prince

\newcommand{\asinglehonour}{A single Honour}


%%% MOUNTS

% Dragon

\newcommand{\dragonnote}{Dragon and Ancient Dragon share the same \zerotoXmountsperarmy{X} limitation.}

% Sky Sloop

\newcommand{\skyreaper}{Sky Reaper}
\newcommand{\skyreaperdef}{%
\range{24}, \shots{4}, \St{} 5, \AP{} 3, \textbf{\quicktofire}.%
}


%%% CORE

% Sea Guard

\newcommand{\steadyaim}{Steady Aim}
\newcommand{\steadyaimdef}{%
The model can shoot from the third rank (in addition to the first and second) and it does not suffer to-hit penalties for Stand and Shoot Charge Reactions.%
}

\newcommand{\covervolley}{Cover Volley}
\newcommand{\covervolleydef}{%
When an enemy unit declares a Charge against a unit with \martialdiscipline{}, a single friendly unit containing one or more models with \covervolley{} may immediately perform a Stand and Shoot Charge Reaction with the following conditions and restrictions:%
\begin{smallitemize}%
\item The distance between the Charger and the Charged unit \textbf{must} be greater than the Charger's Advance Rate (using the lowest value among the Charging models if there is more than one).%
\item The unit with \covervolley{} is within \distance{12} of the Charged unit.%
\item Only models with \covervolley{} may shoot.%
\item The unit \textbf{must} use Stand and Shoot before the Charged unit declares its Charge Reaction. If the Charge is no longer possible after the unit's Stand and Shoot (e.g. due to the Charging unit being destroyed or failing a Panic Test), the Charged unit does not declare any Charge Reaction.%
\item The Stand and Shoot Charge Reaction is performed as if the enemy had declared the Charge against the unit with \covervolley{} in their current position (apply the normal rules for the Stand and Shoot Charge Reaction, i.e. the Charging unit must be Located in the Front Arc of the unit with \covervolley{}, the unit with \covervolley{} cannot be Shaken or Fleeing, etc.).
\end{smallitemize}%
}


%%% SPECIAL

% Sword Masters

\newcommand{\swordsworn}{Sword Sworn}
\newcommand{\swordsworndef}{%
The model part gains a +1 to-hit modifier when attacking with a \gw{}.%
}

% Lion Guard

\newcommand{\gainhighlandersandlosescoring}{Gain \textbf{\baleighighlanders{}} and lose \scoring{}}
\newcommand{\highprincegeneral}{\highprince{} that is the \general{}}% both conditions must be met

\newcommand{\baleighighlanders}{Baleig Highlanders}
\newcommand{\baleighighlandersdef}{%
The model gains \hardtarget{} (1), \lighttroops{}, and \skirmisher{}.%
}

%%% QUEEN'S BOWS

% Nothing special


%%% NAVAL ORDNANCE

% Sea Guard Reaper

\newcommand{\elvenboltthrower}{Elven Bolt Thrower}
\newcommand{\elvenboltthrowerdef}{%
This Artillery Weapon can be fired in two ways:%
\begin{smallitemize}%
\item \range{48}, \shots{1}, \St{} 3 [6], \AP{} 10, \textbf{\areaattack{} (1\timess{}5)}, [\textbf{\multiplewounds{D3}{}}]%
\item \range{48}, \shots{6}, \St{} 4, \AP{} 2%
\end{smallitemize}%
}


%%% ANCIENTS ALLIES

\newcommand{\rebirth}{Rebirth}
\newcommand{\rebirthdef}{%
The first time a \phoenix{} loses its last Health Point, the owner \textbf{must} roll a D6.
The roll is successful on a roll of 5+ (or 3+ if the model has \wardensbond{}):
\begin{smallitemize}
\item Remove the model as a casualty as usual, but place a marker on the centre of the model's final position.
\item In the next Player Turn, at the start of step 3 of the Movement Phase Sequence (after Rallying Fleeing units), the \phoenix{} model is placed back on the Battlefield. The centre of the model \textbf{must} be placed within \distance{3} of the marker and the model \textbf{must} be placed more than \distance{1} away from other units and Impassable Terrain, facing any direction.
\item If the model cannot be placed following these rules, it cannot return for the rest of the game.
\item The returned model is the same model that left the game, including any and all ongoing effects (such as spells affecting the model), with the exception that it always returns with only 1 Health Point left and counts as Rallied in case it was Fleeing when it lost its last Health Point (and thus is Shaken until the end of the Player Turn).
\item The model does not grant Victory Point for being Destroyed if it still has Health Points left at the end of the game.
\end{smallitemize}
If the roll fails, follow the normal rules (i.e. the model is removed as a casualty).%
}

\newcommand{\firephoenix}{Fire Phoenix}
\newcommand{\firephoenixdef}{%
The model gains \textbf{\aegis{} (2+, \against{} \flamingattacks{})}, \textbf{\flamingattacks}, and \textbf{\grindattacks{} (D6)}.\newline%
The model may perform a \sweepingattack{}. The enemy unit suffers D6 hits and an additional D3 hits for each rank after the first.\newline%
The Grind Attacks and Sweeping Attacks are resolved with Strength 4, Armour Penetration 1, and \textbf{\flamingattacks}.%
}

\newcommand{\frostphoenix}{Frost Phoenix}
\newcommand{\frostphoenixdef}{%
The model gains \textbf{\aegis{} (5+)}, \textbf{\fearless{}}, and \textbf{\supernal{}}. Enemy units in base contact with one or more Frost Phoenixes suffer \minuss{}2 Agility, \minuss{}2 Offensive Skill, and \minuss{}2 Defensive Skill.%
}

\newcommand{\wardensbond}{Warden's Bond}
\newcommand{\warden}{Warden}
\newcommand{\wardensbonddef}{%
The model gains +1 Discipline, \textbf{\martialdiscipline}, and passes its \rebirth{} roll on 3+ instead of 5+. The Phoenix model part gains \textbf{\harnessed}. The model gains an additional model part:\newline%
\wardenprofile{}%
}
