
% Unit Entry Names

% Characters

\newcommand{\greatkhan}{Great Khan}

\newcommand{\khan}{Khan}

\newcommand{\shaman}{Shaman}

\newcommand{\mammothhunter}{Mammoth Hunter}

% Mounts

\newcommand{\tusker}{Tusker}

\newcommand{\rockaurochs}{Rock Aurochs}

% Core

\newcommand{\tribesmen}{Tribesmen}
\newcommand{\tribesman}{Tribesman}

\newcommand{\bruisers}{Bruisers}
\newcommand{\bruiser}{Bruiser}

\newcommand{\scraplings}{Scraplings}
\newcommand{\scrapling}{Scrapling}

\newcommand{\scraplingforeman}{Scrapling Foreman}

% Special

\newcommand{\mercenaryveterans}{Mercenary Veterans}
\newcommand{\mercenaryveteran}{Mercenary Veteran}

\newcommand{\tuskercavalry}{Tusker Cavalry}
\newcommand{\rider}{Rider}

\newcommand{\yetis}{Yetis}
\newcommand{\yeti}{Yeti}

\newcommand{\scraplingtrappers}{Scrapling Trappers}
\newcommand{\scraplingtrapper}{Scrapling Trapper}

\newcommand{\sabretoothtigers}{Sabretooth Tigers}
\newcommand{\sabretoothtiger}{Sabretooth Tiger}

\newcommand{\kineater}{Kin-Eater}

% Powder Keg

\newcommand{\thundercannon}{Thunder Cannon}
\newcommand{\bombardiercrew}{Bombardier Crew}
\newcommand{\woollyrhino}{Woolly Rhino}
\newcommand{\chassis}{Chassis}

\newcommand{\scratapult}{Scratapult}
\newcommand{\scraplingcrew}{Scrapling Crew}

\newcommand{\bombardiers}{Bombardiers}
\newcommand{\bombardier}{Bombardier}

%Chained Beasts

% Rock Aurochs defined in Mounts

\newcommand{\frostmammoth}{Frost Mammoth}

\newcommand{\slavegiant}{Slave Giant}

% Unit Specific Model Rules

% Great Khan and Khan

\newcommand{\asinglebigname}{A single Big Name}

% Hunter

\newcommand{\loner}{Loner}
\newcommand{\lonerdef}{%
	If on foot, the model can only join units of Yetis and Sabretooth Tigers; ignore the Insignificant rule for joining units. If mounted, it cannot join any unit. A model with Loner cannot join a unit containing any other Characters, and Characters cannot join a unit containing a model with Loner.%
}

\newcommand{\animalmaster}{Animal Master}
\newcommand{\animalmasterdef}{%
	The model gains \textbf{\commandingpresence{}}, but only units of Sabretooth Tigers may benefit from it.%
}

\newcommand{\leaderofthepack}{Leader of the Pack}
\newcommand{\leaderofthepackdef}{%
	The Mammoth Hunter's base size is changed to 50\timess{}50 \si{\milli\meter}. As long the model is joined to a unit of Sabretooth Tigers, the unit (including the Mammoth Hunter) gains \textbf{\swiftreform{}} and \textbf{\vanguard{}}, and the Mammoth Hunter counts as being a Standard Beast for the purposes of distributing hits, except for Stomp Attacks.%
}

\newcommand{\themodelloseslighttroops}{The model loses \lighttroops{}.}

% Rock Aurochs

\newcommand{\livingavalanche}{Living Avalanche}
\newcommand{\livingavalanchedef}{%
	The model's Impact Hits gain +1 Strength and +1 Armour Penetration.%
}

% Scraplings

\newcommand{\profilebelow}{profile below}

\newcommand{\foremannote}{The Scrapling Foreman is an option for Scrapling units.}
\newcommand{\backtowork}{Back to Work!}
\newcommand{\backtoworkdef}{%
	The Scrapling Foreman is a Champion, except it does not benefit from First Among Equals. It gains \textbf{\rallyaroundtheflag{}}, but only Scraplings, Scrapling Trappers, and Scratapults may benefit from it.%
}

% Mercenary Veterans

\newcommand{\mercenaryveteranscategorynote}{%
	When equipped with Braces of Ogre Pistols, \mercenaryveterans{} also count towards Powder Keg and their maximum unit size is reduced to 6 models.%
}
\newcommand{\battlescarred}{Battle-Scarred}
\newcommand{\battlescarreddef}{%
	Each unit of \mercenaryveterans{} may be given up to two of the upgrades listed below (the upgrades \textbf{must} be written on the Army List). The models gain:%
	\raggedcolumns%
	\begin{multicols}{2}%
	\begin{itemize}%
		\item \accurate{}
		\item \devastatingcharge{} (+1 \St{}, +1 \AP{})
		\item \lethalstrike{}
		\item \magicresistance{} (2)
		\item \pa{}
		\item \poisonattacks{}
		\item \swiftstride{}
		\item \vanguard{}
	\end{itemize}%
	\end{multicols}%
	Each upgrade may only be taken by a single unit of \mercenaryveterans{} in your army.%
}

% Yetis

\newcommand{\touchoffrost}{Touch of Frost}
\newcommand{\touchoffrostdef}{%
	Enemy units suffer \minuss{}1 Agility for each unit of Yetis in base contact with them.%
}

% Scrapling Trappers

\newcommand{\itsatrap}{It's a Trap!}
\newcommand{\itsatrapdef}{%
	Each unit of Scrapling Trappers may place a Trap Counter:%
	\begin{itemize}%
	\item Right before the battle (during step 7 of the Deployment Phase Sequence), on a single Terrain Feature other than Open Terrain that the unit was deployed in or was in contact with at any point during its Vanguard move%
	\item Once during each friendly Movement Phase, on a single Terrain Feature other than Open Terrain that the unit was in contact with during an Advance Move, March Move, or a Reform in this phase%
	\end{itemize}%
	If an enemy unit performs an Advance Move, March Move, Reform, Pivot, Charge Move, Failed Charge Move, Pursuit Move, or Flee Move inside or into contact with a Terrain Feature with one or more Trap Counters, remove all Trap Counters in that particular Terrain Feature. Each model in the unit \textbf{must} take a Dangerous Terrain (1) Test. These tests are not considered to be caused by the Terrain Feature; any Dangerous Terrain Tests that would normally be caused by the Terrain Feature still need to be taken.%
}

% Thunder Cannon

\newcommand{\thundercannondef}{%
	This Artillery Weapon can be fired in two ways:%
	\begin{smallitemize}%
		\item \textbf{\cannon{}}, \range{48}, \shots{1}, \St{} 5 [10], \AP{} 2 [10], \textbf{\areaattack{1\timess{}5}}, [\textbf{\multiplewounds{D3+1, \clippedwings{}}{}}]
		\item \textbf{\volleygun{}}, \range{12}, \shots{2D6}, \St{} 5, \AP{} 4
	\end{smallitemize}%
	A Thunder Cannon that only Pivots (and moves no further) during its owner's Movement Phase ignores the to-hit modifier from Moving and Shooting in the next Shooting Phase.%
}

% Scratapult

\newcommand{\scratapultdef}{%
	\textbf{\catapult{5\timess{}5}}, \range{12--48}, \shots{1}, \St{} 3, \AP{} 1, \textbf{\lethalstrike{}}.\newline
	A Scratapult that only Pivots (and moves no further) during its owner's Movement Phase ignores the to-hit modifier from Moving and Shooting in the next Shooting Phase.%
}

% Bombardiers

\newcommand{\handcannon}{Hand Cannon}
\newcommand{\handcannondef}{%
	\range{24}, \shots{D6}, \St{} 4, \AP{} 2, \textbf{\quicktofire{}}.%
}

% Rock Aurochs

\newcommand{\theridermusttake}{The Rider \textbf{must} take}
\newcommand{\rockaurochsrestriction}{\zerotoXunitsperarmy{1} if it includes any Characters mounted on a Rock Aurochs.}

% Frost Mammoth

\newcommand{\eachridermusttake}{Each Rider \textbf{must} take}

\newcommand{\freezingaura}{Freezing Aura}
\newcommand{\freezingauradef}{%
	The model can cast \spellformat{\shamanismspellfour{}}{\shamanism{}} as a Bound Spell with Power Level (4/8). Enemy units within \distance{9} of one or more Frost Mammoths suffer \minuss{}3 Agility. The roll for Flee Distance of enemy units that Break from Combat while in base contact with one or more Frost Mammoths is subject to Minimised Roll.%
}

% Slave Giant

\newcommand{\giantseegiantdo}{Giant See, Giant Do}
\newcommand{\giantseegiantdodef}{%
	The model gains \textbf{\sonsoftheavalanche{}} and counts as a Character for the purpose of \sonsoftheavalanche{}.\newline%
	The model is a \textbf{\musician{}}. The range of the model's March to the Beat, and to enemy units that are required to take a March Test due to the Slave Giant, are both extended to \distance{18}.%
}

\newcommand{\rage}{Rage}
\newcommand{\ragedef}{%
	Whenever the model loses a Health Point, it gains +1 Attack Value. Whenever it gains a Health Point, it suffers \minuss{}1 Attack Value.%
}

\newcommand{\bigbrother}{Big Brother}
\newcommand{\bigbrotherdef}{%
	The model's Health Points are \textbf{set} to 8, and its base size is changed to 75\timess{}100 \si{\milli\meter}.\newline%
	The roll for the number of hits from its Stomp Attacks is subject to Maximised Roll.%
}

\newcommand{\giantclub}{Giant Club}
\newcommand{\giantclubdef}{%
	Attacks made with this weapon gain +1 Strength and +1 Armour Penetration.%
}
