% Army Model Rule Names

\newcommand{\scraplinglookout}{Scrapling Lookout}
\newcommand{\mountainhide}{Mountain Hide}
\newcommand{\sonsoftheavalanche}{Sons of the Avalanche}
\newcommand{\ironfist}{Iron Fist}
\newcommand{\braceofogrepistols}{Brace of Ogre Pistols}
\newcommand{\ogrecrossbow}{Ogre Crossbow}
\newcommand{\huntingspear}{Hunting Spear}
\newcommand{\asinglebigname}{A single Big Name}

% Army Model Rule Texts

\newcommand{\scraplinglookoutdef}{%
If a unit includes a \standardbearer{} or a \bsb{} with \scraplinglookout{}, there must be fewer than 3 \rnf{} models before hits can be distributed onto \characters{} with the same \type{} and \Height{} as the unit.
}

\newcommand{\mountainhidedef}{%
When a model with \mountainhide{} suffers a wound from an attack with \multiplewounds{}, the number of wounds that it is multiplied into (due to \multiplewounds{}) is halved, rounding up.
}

\newcommand{\sonsoftheavalanchedef}{%
The model part gains \impacthits{1}. If its unit has 2 or more Full Ranks, the model part gains \impacthits{2}. a character with \sonsoftheavalanche{} instead gains \impacthits{D3}, or \impacthits{D3+1} if its unit has 2 or more Full Ranks. In addition, the model is immune to the effects of \fear{} from enemy models.
}

\newcommand{\ironfistdef}{%
The wielder gains +1 Armour and +1 Attack Value unless using another weapon. If the wielder is on foot, it also gains Parry.\newline
This weapon cannot be enchanted with \weaponenchantment{} from the Common \specialequipment{} section.}

\newcommand{\braceofogrepistolsdef}{%
\range{24}, \shots{2}, \St{} 4, \AP{} 2, \textbf{\quicktofire{}}. Counts as \pw{} in Close Combat.
}

\newcommand{\ogrecrossbowdef}{%
\range{30}, \shots{1}, \St{} 2 [5], \AP{} 1 [3], \textbf{\areaattack{1\timess{}5}}.
}

\newcommand{\huntingspeardef}{%
\range{12}, \shots{1}, \St{} as user +1, \AP{} as user +1, \textbf{Quick to Fire}, \textbf{Multiple Wounds (D3, against Gigantic)}.
}


% Unit Specific Model Rules Names

\newcommand{\loner}{Loner}
\newcommand{\animalmaster}{Animal Master}
\newcommand{\leaderofthepack}{Leader of the Pack}
\newcommand{\battlescarred}{Battle-Scarred}
\newcommand{\touchoffrost}{Touch of Frost}
\newcommand{\itsatrap}{It's a Trap!}
\newcommand{\handcannon}{Hand Cannon}
\newcommand{\livingavalanche}{Living Avalanche}
\newcommand{\freezingaura}{Freezing Aura}
\newcommand{\giantseegiantdo}{Giant See, Giant Do}
\newcommand{\rage}{Rage}
\newcommand{\bigbrother}{Big Brother}
\newcommand{\giantclub}{Giant Club}
\newcommand{\backtowork}{Back to Work!}


% Unit Specific Model Rules

\newcommand{\lonerdef}{%
A model on foot with Loner can only join units of Yetis and Sabretooth Tigers (ignore the Insignificant rule for joining units). If mounted, it cannot join any unit. A model with Loner cannot join a unit containing any other Characters, and Characters cannot join a unit containing a model with Loner.
}

\newcommand{\animalmasterdef}{%
The model gains Commanding Presence, but only units of Sabertooth Tigers may benefit from it.
}

\newcommand{\leaderofthepackdef}{%
The Mammoth Hunter changes its base size to 50\timess{}50\si{\milli\meter}. As long the model is part of a unit of Sabretooth Tigers, the unit (including the Mammoth Hunter) gains Swift Reform and Vanguard, and the Mammoth Hunter counts as being Standard Beast for the purposes of distributing hits.
}

\newcommand{\battlescarreddef}{%
Each unit of \mercenaryveterans{} \textbf{must} be given two of the following upgrades listed below (written on the Army List). The model gains :
\begin{itemize}
\item \accurate{}
\item \devastatingcharge{+1 Str, +1 AP}{}
\item \lethalstrike{}
\item \magicresistance{2}{}
\item \pa{}
\item \poisonattacks{}
\item \swiftstride{}
\item \vanguard{}
\end{itemize}
Each upgrade may only be taken by a single unit of \mercenaryveterans{} in your army.
}

\newcommand{\touchoffrostdef}{%
Enemy units suffer \minuss{}1 Agility for each unit of Yetis May upgrade one model to a Champion in base contact with them.
}

\newcommand{\itsatrapdef}{%
Each unit of Scrapling Trappers may place a Trap Counter:
\begin{itemize}
\item{right before the battle (during step 7 of the Deployment Phase Sequence), on a single Terrain Feature other than Open Terrain that the unit was deployed in or was in base contact with at any point during its Vanguard move, and}
\item{once during each friendly Movement Phase, on a single Terrain Feature other than Open Terrain that the unit was in base contact with at any point during this phase after an Advance Move, March Move, or a Reform.}
\end{itemize}
If an enemy unit makes an Advance Move, March Move, Reform, Pivot, Charge Move, Failed Charge Move, Pursuit Move, or Flee Move inside or into base contact with a Terrain Feature with one or more Trap Counters, remove all Trap Counters in that particular Terrain Feature. Each model in the unit must take a Dangerous Terrain (1) Test (these tests are not considered to be caused by the Terrain Feature; any Dangerous Terrain Tests that would normally be caused by the Terrain Feature still need to be taken).
}

\newcommand{\handcannondef}{%
\range{24}, \shots{D6}, \St{} 4, \AP{} 2, \textbf{Quick to Fire}.
}

\newcommand{\thundercannondef}{%
This Shooting Weapon can be fired in two ways:%
\begin{itemize}
\item As a \textbf{\cannon{}} Artillery Weapon with \range{48}, \shots{1}, \St{} 5 [10], \AP{} 2 [10], \textbf{\areaattack{1\timess{}5}}, [\textbf{\multiplewounds{D3+1, \clippedwings{}}{}}].
\item As an Artillery Weapon with \range{12}, \shots{2D6}, \St{} 5, \AP{} 4.
\end{itemize}
A Thunder Cannon that only Pivots (and moves no further) during its owner’s Movement Phase ignores the to-hit modifier from Moving and Shooting in the next Shooting Phase.
}

\newcommand{\scratapultdef}{%
\textbf{\catapult{5\timess{}5}} with \range{12--48}, \shots{1}, \St{} 3, \AP{} 1, \textbf{Lethal Strike}.\newline
A Scratapult that only Pivots (and moves no further) during its owner’s Movement Phase ignores the to-hit modifier from Moving and Shooting in the next Shooting Phase.
}

\newcommand{\livingavalanchedef}{%
Impact Hits from the model gain +1 Strength and +1 Armour Penetration.
}

\newcommand{\replaceoxbowwonechoice}{\optionschoice{The Rider may replace its \ogrecrossbow{} with \onechoiceonlyNOC{}:}}
\newcommand{\anyreplaceoxbowwonechoice}{Any Rider may replace its Ogre Crossbow with}

\newcommand{\freezingauradef}{%
The model can cast \textit{Chilling Howl} from Shamanism as a Bound Spell with Power Level (4/8).\newline
Enemy units within 9” of one or more Frost Mammoths suffer \minuss{}3 Agility. The roll for Flee Distance of enemy units that Break from Combat while in base contact with one or more Frost Mammoths is subject to Minimised Roll.
}

\newcommand{\giantseegiantdodef}{%
The model gains Sons of the Avalanche and counts as a Character for the purpose of Sons of the Avalanche.\newline
The model is a Musician. The range of the Giant's March to the Beat, and to enemy units that are required to take a March Test due to the Slave Giant, are both extended to \distance{18}. 
}

\newcommand{\ragedef}{%
Whenever the model loses a Health Point, it gains +1 Attack Value. Whenever it gains a Health Point, it suffers \minuss{}1 Attack Value.
}

\newcommand{\bigbrotherdef}{%
The model's Health Points are \textbf{set} to 8, and its base size is changed to 75x100mm.\newline
The roll for the number of hits from its Stomp Attacks is subject to Maximised Roll.
}

\newcommand{\giantclubdef}{%
Attacks made with this weapon gain +1 Strength and +1 Armour Penetration.
}

\newcommand{\backtoworkdef}{%
The Scrapling Foreman is a Champion, except it does not benefit from First Among Equals. It gains Rally Around the Flag, but only Scraplings, Scratapults, and Scrapling Trappers may benefit from it.
}